### 2015-05-11 CacadedTunableFilter.tex
Initial git uplaod

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%          File: CascadedTunableFilter.tex            	%
%                  Date: 2 Feb, 2015                	%
%                                                    	%
%   For submission to a journal  						%
%                                                     	%
%   Technical paper about the results obtained with   	%
%   professor Wei Shi with tunable cascaded				%
%	contra-directional coupler				      		%
%	+ theorical analysis								%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\documentclass[letterpaper,10pt]{article}
\documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1}
%\usepackage{osameet2}

\usepackage{amsmath,amssymb}
\newcommand{\me}{\mathrm{e}}
\newcommand*\diff{\mathop{}\!\mathrm{d}}

\usepackage[utf8]{inputenc} %encoding of the input(this text file)
\usepackage[T1]{fontenc} 	%uses the right font encoding
\usepackage{lmodern,textcomp}		%makes font work for fontenc
\usepackage[french,english]{babel} %multiple languages
\selectlanguage{english}	%can switch to french later using this
\usepackage{graphicx,epsfig,epstopdf}
%\usepackage{caption,subcaption}

%\usepackage[numbers]{natbib}
%\renewcommand{\bibfont}{\footnotesize}
%\setlength{\bibsep}{2.0pt}

\begin{document}
\title{Widely Bandwidth-Tunable Broadband Optical Filter on Silicon}
%\date{14/10/2014}

\author{Jonathan St-Yves} 
\author{Hadi Bahrami}
\author{Philippe Jean}
\author{Sophie Larochelle}
\author{Wei Shi}\email{Corresponding author: wei.shi@gel.ulaval.ca}
\affiliation{Centre d'optique, photonique et laser (COPL) and Département de génie électrique et génie informatique, Université Laval, 2375 rue de la Terrasse, Québec (Québec), Canada, G1V 0A6}

\begin{abstract}
We demonstrate an integrated silicon tunable band-pass filter with low in-band ripples of 0.3 dB, a high contrast of 55 dB, and no free-spectral range. A record bandwidth tuning from 788 to 117 GHz was achieved.
\end{abstract}

\pacs{ (130.7408) Wavelength filtering devices; (350.2770) Gratings}

%\linespread{0.95}		%Space saving emergency line

\maketitle

%\section{Introduction}

Optical filters are essential components for optical communication applications such as wavelength-division multiplexing (WDM), signal processing, and dynamic bandwidth allocation \cite{DynamicBW}.
These key devices are now needed in integrated photonic systems, in this case, on the silicon-on-insulator platform (SOI), to achieve the same functions as traditional discrete optical components such as diffractive grating spectrometers. 
Silicon photonics allows for CMOS compatible mass fabrication for low cost, high yield, and large-scale on-chip integration. 
Future high-capacity transmission systems, e.g., applying the super-channel technique, will require a dynamic channel bandwidth allocation over a few hundred gigahertz \cite{jinno2009spectrum}. 
However, large bandwidth tunability is currently only available in bulky bench-top systems. Existing integrated tunable filters, e.g., using microring resonators and MZ interferometers, have relatively small tunable bandwidth (less than 200 GHz)  \cite{ong2013ultra}. 
Also, their free spectral ranges (FSRs) are small, typically less than 10 nm \cite{ong2013ultra}.

Contra-directional couplers(contra-DCs) are grating-assisted add-drop filters \cite{shi2013siliconContraDC}. 
Analogous to waveguide Bragg gratings, the wavelength selectivity in contra-DCs are based on periodic dielectric perturbations. But instead of backreflections in the same waveguide, the selected wavelength in a contra-DC is dropped to another waveguide through contra-directional coupling.
This allows add-drop operation without the need of a circulator. 
Contra-DCs have merits of compactness, flat-top response, flexible filter design (e.g, through apodization), and near-infinite FSR (in the case of first-order gratings).
In particular, they allow for very high bandwidths (greater than 10 nm) and thus can support very-high-baud-rate super-channel signals \cite{jinno2009spectrum}.
In this paper, we demonstrate a broadband filter with a large tunability in both wavelength and channel bandwidth, using thermally controlled cascaded contra-DCs on a silicon chip. The filter has flat-top responses, low insertion loss, low in-band ripples, and high contrast between the pass-band and the stop-band.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1.00\columnwidth]{data/CascadedSchematic2}
	\centering
	\caption{Schematic of the device. The dropped wavelength of the first contra-directional coupler is re-filtered in an identical component. Both contra-directional couplers are temperature-controlled with metal heaters. Plots show examples of spectrum at each port, on a logarithmic scale.}
	\label{fig:schematic}
\end{figure}
%\section{Principle and Design}

The schematic of the proposed device is shown in Fig.~\ref{fig:schematic}. 
It consists of a pair of cascaded contra-DCs, each operating as an add-drop filter. 
The drop port of the first contra-DC is connected to the input port of the second contra-DC. 
Therefore, the finally dropped signal is determined by the product of the  drop-port transfer functions of the two contra-DCs. The center wavelength of a contra-DC is determined by the phase-match condition: $\lambda_\text{c} = \Lambda (n_\text{1}+n_\text{2})$, where $\lambda_\text{c}$ is the center wavelength of contra-directional coupling, $\Lambda$ is the grating pitch, and $n_\text{1}$ and $n_\text{2}$ are the effective refractive indices of the first-order and second-order eigenmodes in the coupler. 
Assuming identical filter designs (i.e., same window functions and parameters) of the cascaded contra-DCs, the bandwidth of the finally dropped signal can be tuned by detuning their center wavelengths.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\columnwidth]{data/FigApod}
  \caption{(Top)SEM photography of a part of the grating. The contra-directional coupler consists of two close waveguides of different width with periodic sidewall corrugations. (Bottom Left) Apodization profile of the grating. A larger coupling requires larger corrugations. (Bottom right) Average electric field in both waveguides. }
  \label{fig:SEM}
\end{figure}

A broadband filter design for a coarse WDM on the 220-nm SOI platform \cite{shi2013siliconCWDM} is adopted for individual contra-DCs.  
In each contra-DC, the widths of the waveguides are of 560 and 440 nm.
This high asymmetry ensures a negligible forward coupling. 
The gratings are formed by sidewall corrugations in strip waveguides with a pitch of 312 nm. 
The spacing between the waveguides varies between 65 and 135 nm with a Gaussian profile as shown in Fig.~\ref{fig:SEM} for efficient sidelobe suppression, for which details can be found in \cite{shi2013siliconCWDM}.
The spectral responses of each contra-DC is calculated using coupled mode theory, following the same procedure as in  \cite{shi2013siliconContraDC}, with two additions: apodization and noise simulation.
%The first part in predicting the contra-directional coupler spectrum is to compute the dielectric variation caused by the perturbation $\Delta\varepsilon(x,y)$ which is $\varepsilon_0/\pi*(n_{max}(x,y)^2-n_{min}(x,y)^2)$ where the $1/\pi$ factor is the first Fourier expansion coefficient in the case of a square shaped perturbation. 
%One also needs the mode distribution in each waveguide  $E_1(x,y)$ and $E_2(x,y)$ at the average point of the perturbation, which can be obtained using a 2D eigenmode solver such as Lumerical MODE. 
%The couplings $\kappa_{11}$, $\kappa_{12}$ and $\kappa_{22}$  can then be calculated from
%\begin{equation}\label{eq:coupling}
%\kappa_{nm}=\frac{\omega}{4}\iint \textbf{E}^*_n(x,y)\Delta\varepsilon_1(x,y) \textbf{E}_m(x,y) \diff x \diff y
%\end{equation}

While an unapodized (uniform) grating can be simulated with only two transfer matrices , $S_1$ and $S_2$ \cite{shi2013siliconContraDC}, an apodized one needs both of these matrices for each step along the propagation, to match the change of coupling. 
The first change is thus to modify the transfer matrix of the system to the product of all the grating elements along the propagation axis.
This calculation ideally takes shape in an infinite sum, but for computation simplicity, we use a finite number of steps with different couplings that still approximates the apodization profile with enough accuracy. 
Our simulations uses  steps of constant length $z_i-z_{i-1}=z_c$. 
The total response of a contra-DC $C(z_0,z_n)$ is calculated using the transfer-matrix method, where $E(z_0)=C(z_0,z_n) E(z_n)$.

\begin{equation}[!h]
\label{eq:CMatrix}
 C(z_0,z_n) =  \prod_{i=1}^{n}\me^{S_{1,i}(z_i-z_{i-1})}\me^{S_{2,i}(z_i-z_{i-1})}
\end{equation}

%with $\Delta\hat{\beta}_{1,2} = \frac{2\pi}{\lambda}n_{\text{eff }1,2}-\frac{\pi}{\Lambda}$ and

%\begin{equation}
%S_1= \begin{bmatrix}
%		j\Delta\hat{\beta}_1 & 0 & 0 & 0 \\
%		0 & j\Delta\hat{\beta}_2 & 0 & 0 \\
%		0 & 0 & -j\Delta\hat{\beta}_1 & 0 \\
%		0 & 0 & 0 & -j\Delta\hat{\beta}_2
%	 \end{bmatrix}
%\ end{equation}

%\begin{figure*}[tbp]
%
%\begin{equation}
%\begin{split} 
%S_2= 
%\begin{bmatrix}
%-j\Delta\hat{\beta}_1 & 0 & -j\kappa_{11}\me^{j2\Delta\hat{\beta}_1 z_c} & -j\kappa_{12}\me^{j(\Delta\hat{\beta}_1+\Delta\hat{\beta}_2) z_c} \\
%0 & -j\Delta\hat{\beta}_2 & -j\kappa_{12}\me^{j(\Delta\hat{\beta}_1+\Delta\hat{\beta}_2) z_c} & -j\kappa_{22}\me^{j2\Delta\hat{\beta}_2 z_c} \\
%j\kappa^*_{11}\me^{-j2\Delta\hat{\beta}_1 z_c} & j\kappa^*_{12}\me^{-j(\Delta\hat{\beta}_1+\Delta\hat{\beta}_2) z_c} & j\Delta\hat{\beta}_1 & 0 \\
%j\kappa^*_{12}\me^{-j(\Delta\hat{\beta}_1+\Delta\hat{\beta}_2) z_c} & j\kappa^*_{22}\me^{-j2\Delta\hat{\beta}_2 z_c1} & 0 & j\Delta\hat{\beta}_2
%	 \end{bmatrix}
%\end{split} 
%\end{equation}
%\hrulefill
%\end{figure*}

It is possible to easily add phase noise to the transfer matrix solution by adding random noise to the $\Delta\hat{\beta}$ propagation constants. The frequency distribution of the noise will thus match the quantization steps of the matrices, but since the response noise is dependent of both the amplitude and frequency of the sidewall roughness \cite{simard2011impact},we can match the simulation to the experiment by choosing the right noise amplitude.

On top of each contra-DC sits a metal strip acting as a microheater for thermal tuning.  
The refractive index of silicon has a temperature dependence of 1.87$\times10^{-4}$K$^{-1}$ at room temperature for wavelengths around 1550 nm~\cite{frey2006temperature}.
Without electrical input, the optical responses of the two filters are identical (neglecting fabrication uniformities) resulting in a sharp transition from the pass-band to the stop-band. 
Applying independent electrical currents on the heaters, we can shift the spectra of the contra-DCs simultaneously or differentially for wavelength or bandwidth tuning.
In the ideal case, each contra-DC should be uniformly heated so that the apodization profile does not change as the temperature varies.

%\section{Experiment}

The device was fabricated using a CMOS-compatible technology with electron-beam lithography. 
Fiber grating couplers were used as optical IOs in the measurement. 
Fig.~\ref{fig:passive} shows the measured drop port response of the cascaded contra-DC filters. 
The measurements were normalized using the response of a pair of directly connected fiber grating couplers on the same chip.
\begin{figure}[htbp]
\centering
\includegraphics[width=.99\columnwidth]{data/Passive5NormNoSimu}
\caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz. The red line shows the averaged noise floor.}
\label{fig:passive}
\end{figure}

The device exhibits a high side-lobe suppression ratio (SLSR) of over 40 dB and a high contrast of about 55 dB between the pass-band and the stop-band. 
The insertion loss is very low, less than 0.5 dB (i.e., 0.25 dB per contra-DC), with small ripples of less then 0.3 dB within the 1-dB passband over 5.8 nm (733~GHz). 
The edge roll-off rate is 19 dB/nm on the left side and 24 dB/nm on the right side.
Further work could optimize the grating structure using the inverse layer peeling algorithm\cite{skaar2001synthesis} since the mathematics of the contra-directional coupler are similar to those of Bragg gratings.

By changing the temperature of a single contra-DC, we offset the phase-match condition of a filter, resulting in a smaller band overlap between the two contra-DCs and thus a narrower passband in the drop port, as shown in Fig.~\ref{fig:bandTune}.  
Due to the wavelength detuning,  the stop-band edges are only determined by the single filters. 
As a result, the side-lobes suppression degrades  for small bandwidths but is still better than 15 dB. A continuous tuning of the 3-dB bandwidth from 788 GHz down to 117 GHz (i.e., over 670 GHz or 5.4 nm) is experimentally observed as the on-chip temperature increases by 70 degrees. 
The smallest bandwidth measured in this case was limited by the maximal power delivered before the metal heaters (300-nm-thick, 2-$\mu$m-wide Al strips) were damaged. A smaller bandwidth below 50 GHz should be feasible if more robust heaters are used.
The power efficiency of the bandwidth tuning is about 24 mW/nm, which can significantly improved by optimizing the heater design, e.g., using smaller heater features and thermal isolation \cite{dong2010thermally}.

\begin{figure}[htbp]
\centering
\includegraphics[width=.99\columnwidth]{data/Band5}
\caption{Spectral response of the device for different temperatures applied to only one contra-DC: 1-dB BW tuned down to 65 GHz, 3-dB BW to 117 GHz. The temperatures are obtained from simulation fit.}
\label{fig:bandTune}
\end{figure}

By applying the same temperature variation on both contra-DCs, the center wavelength can be tuned without affecting the filter shape.
As shown in Fig.~\ref{fig:wavTune}, when the center wavelength is continually changed over 4 nm by varying the on-chip temperature, the filter shape is maintained with sharp edges. Actually, slight detuning between the cascaded contra-DCs may be used to compensate for band-edge distortions due to fabrication errors for a more symmetric filter shape. 
The power efficiency of the wavelength tuning is about 44 mW/nm, which is about twice the power consumption of the bandwidth tuning since two contra-DCs are heated simultaneously.
\begin{figure}[htbp]
\centering
\includegraphics[width=.99\columnwidth]{data/Central}
\caption{Spectral response with the heat applied to both contra-DCs: the central wavelength is tuned from 1535 nm to 1539 nm continuously; the temperatures are calculated by comparison to simulation.}
\label{fig:wavTune}
\end{figure}

%\section{Theoretical Performance Limits}

%\subsection{Out of band rejection ratio}
%Limited by \textbf{Apodisation} and Phase Noise.
%A contra-directional coupler spectrum will contain sidelobes corresponding to the Fourier transform of the coupling profile along the propagation axis. 
%Using a constant coupling is analogous to a rectangular window, causing sidelobes of over -15 dB. 
%The use of a Blackman–Nuttall or similar high-order gaussian coupling profile theoretically reduces the sidelobes amplitude to under -50 dB, although electron beam grid resolution distorts the profile by forcing discrete coupling values.

%Still, the dominant cause of weak out of band rejection ratio is phase noise due to sidewall roughness\cite{simard2011impact}. The random change of waveguide width causes the effective index of the modes to jitter, causing a variation of the Bragg-wavelength.

%Both of these effects are added to our simulation using a transfer matrix method. 
%First, multiple matrices are used along the propagation length, with couplings corresponding to the apodization profile.
%Second, the effective index in each of these matrix is randomly varied by an amount corresponding to the roughness amplitude.
%Since the effect of phase noise is dependent on it's spacial frequency \cite{simard2011impact}, and this frequency is based on the matrix discreteness, the simulation noise is calibrated using measurements data.

%As seen in this experiment however, it is possible to greatly improve the out of band rejection ratio by cascading multiple filters together, which adds up the rejection ratio of each, at the cost of making the device longer

%\subsection{In-band insertion loss}
%Limited by length and sidewall roughness loss. 
%The insertion loss in each device at 1550 nm is mainly caused by the material absorption of silicon and scattering loss due to sidewall roughness. 
%The most important parameter to optimize losses is the length of the device, which is often a trade-off for other figures of merit.

%\subsection{Maximal Bandwidth}
%Limited by coupling. Can be enhanced with chirp.
%The bandwidth of the contra-directional coupler is proportional to the coupling between the two waveguides. In practice, the coupling is limited by the field overlap of the first two super-modes as well as the amplitude of the perturbation. Electron beam fabrication allows us to put the waveguides very close to each other, resulting in a large field overlap

%\subsection{Minimal Bandwidth}
%Trade-off with length and phase noise.

%\subsection{Phase/dispertion}
An other important parameter to monitor is the group delay of the device. An uneven delay can cause distortion during detection of the signal, just like dispersion. The simulation and measurements seen in Fig.~\ref{fig:phase} both show a group delay difference of less then 10 ps.
\begin{figure}[tbp]
\centering
\includegraphics[width=.99\columnwidth]{data/Phase}
\caption{ Group delay response of the tunable filter at the drop port. The delay stays within 12 ps between any two points in the band. The out of band results are noisy due to the weak signal.}
\label{fig:phase}
\end{figure}

%\section{Conclusion}
In summary, we have demonstrated a bandwidth tunable filter with a low insertion loss of less then 0.5 dB, low ripples of less than 0.3 dB, a large maximal bandwidth of greater than 750 GHz, and high contrast of 55 dB. 
Compared to other devices based on microring resonators and MZIs, it enables a much larger maximal passband and does not suffer from small FSRs. 
A large bandwidth tuning range over 670 GHz has been achieved, which, to the best of our knowledge, is the widest ever demonstrated on a silicon chip. 
This ultra-wide bandwidth tunability makes the device very attractive for next-generation ultrahigh baud-rate applications (e.g., high-capacity super-channel transmissions) and flexible optical networking.

\begin{table*}[t]
\caption{Recent results with multi-element on-chip silicon filters}
\begin{tabular}{cccccc}
    \hline
	Publication & Filter type & BWmax / FSR & Tunable BW & On-chip loss & Contrast \\
    \hline
    %Ibrahim (2011) &	Cascaded MRs &	0.4 GHz / 10 GHz &	0.6-2 GHz &	0.6 dB &	30 dB
    % \\
    %Alipour (2011) &	Cascaded MRs &	5 GHz / 650 Ghz &	0.8-5 GHz &	1.25-3.75 dB &	38 dB
    % \\
    Ding (2011) &	MRs + MZI &	55 GHz / 1 THz &	28-55 GHz &	3.6 dB &	30 dB
     \\
 	Orlandi (2012) &	MRs + MZI &	173 GHz / 200 GHz &	23-173 GHz &	0.46-1.06 dB &	15-34 dB
      \\
    %Luo (2012) &	Cascaded MRs &	100 GHz / 750 Ghz &	No &	0.3-0.6 dB &	50 dB  \\
    Ong (2013)\cite{ong2013ultra} &	Cascaded MRs &	125 GHz/ 0.9 THz &	11.6-125 GHz &	0.25 dB &	50-100 dB
      \\
    This work & Cascaded contra-DC &	778 GHz / Unlimited  &	117-778 GHz &	0.5 dB &	55 dB \\

    \hline
   \end{tabular}
    \end{table*}

%\subsection{Edge roll-off / Bandwidth effectiveness}

\section*{Acknowledgments}
We acknowledge CMC Microsystems for the  software and the fabrication subsidy. We thank Yun Wang and Lukas Chrostowski with the Univeristy of British Columbia for the fiber grating coupler design. The authors acknowledge the Natural Sciences and Engineering Research Council of Canada, TeraXion and Prompt for funding this research. The silicon chip was fabricated at the University of Washington Microfabrication/Nanotechnology User Facility, a member of the NSF National Nanotechnology Infrastructure Network.

\bibliographystyle{osajnl}
\bibliography{bibli}

\end{document}

### 2015-05-11 data/dataFromFigure.m

@@ -1,0 +1,79 @@
+clc; close all; clear all;
+
+textSizeSmall=14;
+textSizeLarge=16;
+set(0,'defaultFigureColor','w','defaultAxesColor','w');
+set(0,'defaultAxesFontSize',textSizeSmall,'defaultAxesFontName','Helvetica');
+set(0,'defaultFigurePosition',[1200,100,500,400])
+set(0,'defaultAxesYMinorTick','on')
+set(0,'defaultAxesColorOrder',[ 0 0 0; ...
+                                0.8 0 0; ...
+                                0.7 0.6 0; ...
+                                0 0.7 0; ...
+                                0 0 0.8]);
+set(0,'defaultAxesLineStyleOrder','-|--|:');
+set(0,'defaultAxesBox','on'   );
+set(0,'defaultLineLineWidth',2   );
+set(0,'defaultTextFontName','Helvetica' );
+set(0,'defaultTextFontsize',14 );
+
+
+open('DirectCouplers.fig');
+
+h = gcf; %current figure handle   
+axesObjs = get(h, 'Children');  %axes handles
+dataObjs = get(axesObjs, 'Children');
+xdata = get(dataObjs, 'XData');  %data from low-level grahics objects
+ydata = get(dataObjs, 'YData');
+
+normX=xdata; normY=ydata;
+close gcf;
+
+
+open('Filter3Right_0_2V.fig');
+% open('Filter2DUAL.fig');
+
+h = gcf; %current figure handle   
+axesObjs = get(h, 'Children');  %axes handles
+dataObjs = get(axesObjs, 'Children');
+% xdata = get(dataObjs, 'XData');  %data from low-level graphics objects
+% ydata = get(dataObjs, 'YData');
+% xdata = get(dataObjs{2}, 'XData');  %data from low-level graphics objects
+% ydata = get(dataObjs{2}, 'YData');
+% xdata = cell2mat(get(dataObjs, 'XData'));  %data from low-level graphics objects
+% ydata = cell2mat(get(dataObjs, 'YData'));
+xdata = cell2mat(get(dataObjs{2}, 'XData'));  %data from low-level graphics objects
+ydata = cell2mat(get(dataObjs{2}, 'YData'));
+close gcf;
+
+figure1=figure;
+hold all;
+
+%  name={      '+0 K' , ...         %both tuned
+%              '+9 K' , ...
+%              '+24 K' , ...
[…]

### 2015-05-11 data/rawData/dataFromFigure.m

@@ -1,0 +1,81 @@
+clc; close all; clear all;
+
+textSizeSmall=14;
+textSizeLarge=16;
+set(0,'defaultFigureColor','w','defaultAxesColor','w');
+set(0,'defaultAxesFontSize',textSizeSmall,'defaultAxesFontName','Helvetica');
+set(0,'defaultFigurePosition',[1200,100,500,400])
+set(0,'defaultAxesYMinorTick','on');
+set(0,'defaultAxesXMinorTick','on');
+set(0,'defaultAxesColorOrder',[ 0 0 0; ...
+                                0.8 0 0; ...
+                                0.7 0.6 0; ...
+                                0 0.7 0; ...
+                                0 0 0.8]);
+set(0,'defaultAxesLineStyleOrder','-|--|:');
+set(0,'defaultAxesBox','on'   );
+set(0,'defaultAxesTickLength',  [0.015 0.025]   );        
+set(0,'defaultLineLineWidth',1.5   );
+set(0,'defaultTextFontName','Helvetica' );
+set(0,'defaultTextFontsize',14 );
+
+
+open('alignBand.fig');
+
+h = gcf; %current figure handle   
+axesObjs = get(h, 'Children');  %axes handles
+dataObjs = get(axesObjs, 'Children');
+xdata = get(dataObjs, 'XData');  %data from low-level grahics objects
+ydata = get(dataObjs, 'YData');
+
+normX=xdata; normY=ydata;
+close gcf;
+
+
+open('BestTuningEver.fig');
+% open('Filter2DUAL.fig');
+
+h = gcf; %current figure handle   
+axesObjs = get(h, 'Children');  %axes handles
+dataObjs = get(axesObjs, 'Children');
+% xdata = get(dataObjs, 'XData');  %data from low-level graphics objects
+% ydata = get(dataObjs, 'YData');
+% xdata = get(dataObjs{2}, 'XData');  %data from low-level graphics objects
+% ydata = get(dataObjs{2}, 'YData');
+xdata = cell2mat(get(dataObjs, 'XData'));  %data from low-level graphics objects
+ydata = cell2mat(get(dataObjs, 'YData'));
+% xdata = cell2mat(get(dataObjs{2}, 'XData'));  %data from low-level graphics objects
+% ydata = cell2mat(get(dataObjs{2}, 'YData'));
+close gcf;
+
+figure1=figure;
+hold all;
+
[…]

### 2015-05-11 data/dataFromFigure.m
Cleanup

@@ -1,79 +1,0 @@
-clc; close all; clear all;
-
-textSizeSmall=14;
-textSizeLarge=16;
-set(0,'defaultFigureColor','w','defaultAxesColor','w');
-set(0,'defaultAxesFontSize',textSizeSmall,'defaultAxesFontName','Helvetica');
-set(0,'defaultFigurePosition',[1200,100,500,400])
-set(0,'defaultAxesYMinorTick','on')
-set(0,'defaultAxesColorOrder',[ 0 0 0; ...
-                                0.8 0 0; ...
-                                0.7 0.6 0; ...
-                                0 0.7 0; ...
-                                0 0 0.8]);
-set(0,'defaultAxesLineStyleOrder','-|--|:');
-set(0,'defaultAxesBox','on'   );
-set(0,'defaultLineLineWidth',2   );
-set(0,'defaultTextFontName','Helvetica' );
-set(0,'defaultTextFontsize',14 );
-
-
-open('DirectCouplers.fig');
-
-h = gcf; %current figure handle   
-axesObjs = get(h, 'Children');  %axes handles
-dataObjs = get(axesObjs, 'Children');
-xdata = get(dataObjs, 'XData');  %data from low-level grahics objects
-ydata = get(dataObjs, 'YData');
-
-normX=xdata; normY=ydata;
-close gcf;
-
-
-open('Filter3Right_0_2V.fig');
-% open('Filter2DUAL.fig');
-
-h = gcf; %current figure handle   
-axesObjs = get(h, 'Children');  %axes handles
-dataObjs = get(axesObjs, 'Children');
-% xdata = get(dataObjs, 'XData');  %data from low-level graphics objects
-% ydata = get(dataObjs, 'YData');
-% xdata = get(dataObjs{2}, 'XData');  %data from low-level graphics objects
-% ydata = get(dataObjs{2}, 'YData');
-% xdata = cell2mat(get(dataObjs, 'XData'));  %data from low-level graphics objects
-% ydata = cell2mat(get(dataObjs, 'YData'));
-xdata = cell2mat(get(dataObjs{2}, 'XData'));  %data from low-level graphics objects
-ydata = cell2mat(get(dataObjs{2}, 'YData'));
-close gcf;
-
-figure1=figure;
-hold all;
-
-%  name={      '+0 K' , ...         %both tuned
-%              '+9 K' , ...
-%              '+24 K' , ...
[…]

### 2015-05-11 CacadedTunableFilter.tex
IgnoreFile

@@
   \includegraphics[width=1\columnwidth]{data/FigApod}
-  \caption{(Top)SEM photography of a part of the grating.
+  \caption{(a)SEM photography of a part of the grating.
 The contra-directional coupler consists of two close waveguides of different width with periodic sidewall corrugations.
-(Bottom Left) Apodization profile of the grating.
+(b) Apodization profile of the grating.
 A larger coupling requires larger corrugations.
-(Bottom right) Average electric field in both waveguides.
+(c) Intensity distributions of electrical fields of the first and second transverse modes.
 }
@@
 \centering
-\includegraphics[width=.99\columnwidth]{data/Passive5NormNoSimu}
-\caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz. The red line shows the averaged noise floor.}
+\includegraphics[width=.99\columnwidth]{data/Passive6}
+\caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz.}
 \label{fig:passive}

### 2015-05-19 CacadedTunableFilter.tex
Temp Inset and Fixes bib

@@
 The spacing between the waveguides varies between 65 and 135 nm with a Gaussian profile as shown in Fig.~\ref{fig:SEM} for efficient sidelobe suppression, for which details can be found in \cite{shi2013siliconCWDM}.
-The spectral responses of each contra-DC is calculated using coupled mode theory, following the same procedure as in  \cite{shi2013siliconContraDC}, with two additions: apodization and noise simulation.
+The spectral responses of each contra-DC is calculated using coupled mode theory, following the same procedure as in  \cite{shi2013siliconContraDC}, with three additions: apodization, temperature and noise simulation.
+
 %The first part in predicting the contra-directional coupler spectrum is to compute the dielectric variation caused by the perturbation $\Delta\varepsilon(x,y)$ which is $\varepsilon_0/\pi*(n_{max}(x,y)^2-n_{min}(x,y)^2)$ where the $1/\pi$ factor is the first Fourier expansion coefficient in the case of a square shaped perturbation.
@@
 
-\begin{equation}[!h]
+\begin{equation}
 \label{eq:CMatrix}
@@
 The device was fabricated using a CMOS-compatible technology with electron-beam lithography. 
-Fiber grating couplers were used as optical IOs in the measurement. 
+Fiber grating couplers\cite{zhong2014focusingFGC} were used as optical IOs in the measurement. 
 Fig.~\ref{fig:passive} shows the measured drop port response of the cascaded contra-DC filters. 
@@
 \centering
-\includegraphics[width=.99\columnwidth]{data/Band5}
+\includegraphics[width=.99\columnwidth]{data/Band6}
 \caption{Spectral response of the device for different temperatures applied to only one contra-DC: 1-dB BW tuned down to 65 GHz, 3-dB BW to 117 GHz. The temperatures are obtained from simulation fit.}
@@
 In summary, we have demonstrated a bandwidth tunable filter with a low insertion loss of less then 0.5 dB, low ripples of less than 0.3 dB, a large maximal bandwidth of greater than 750 GHz, and high contrast of 55 dB.
-Compared to other devices based on microring resonators and MZIs, it enables a much larger maximal passband and does not suffer from small FSRs. 
+Compared to other devices based on microring resonators and MZIs (see Table \ref{table:comparison}), it enables a much larger maximal passband and does not suffer from small FSRs. 
 A large bandwidth tuning range over 670 GHz has been achieved, which, to the best of our knowledge, is the widest ever demonstrated on a silicon chip. 
@@
     \hline
+    \label{table:comparison}
    \end{tabular}

### 2015-05-19 osa-revtex4-1.tex
Revert "To remove"
This reverts commit 5dcf1c456a8a6675125f266bcb7a71159758cf36.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                         File: osa-revtex4-1.tex                             %
%                        Date: April 15, 2013                                 %
%                                                                             %
%                              BETA VERSION!                                  %
%                   JOSA A, JOSA B, Applied Optics, Optics Letters            %
%                                                                             %
%            This file requires the substyle file osajnl4-1.rtx,              %
%                   running under REVTeX 4.1 and LaTeX 2e                     %
%                                                                             %
%                   USE THE FOLLOWING REVTeX 4-1 OPTIONS:                     %
% \documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1}%
%                    %% Use 11pt for Applied Optics                           %
%                                                                             %
%               (c) 2013 The Optical Society of America                       %
%                                                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1} %% use 11pt for Applied Optics
%%\documentclass[osajnl,preprint,showpacs,superscriptaddress,12pt]{revtex4-1} %% use 12pt for preprint option
\usepackage{amsmath,amssymb,graphicx}
\begin{document}

\title{Preparing a REV\TeX{}4-1 manuscript
for the OSA journals \\ JOSA A, JOSA B, \textit{Optics Letters}, and
\textit{Applied Optics} }

\author{Joe Richardson}
\affiliation{Peer Review, Optical Society of America, 2010 Massachusetts Avenue, NW,
Washington, D.C. 20036, USA}

\author{Chris Videll}\email{Corresponding author: xyx@osa.org}
\author{Jennifer Mayfield}
\affiliation{Publishing Production Services, Optical Society of America,  2010 Massachusetts Avenue, NW,
Washington, D.C. 20036, USA}

\begin{abstract}This template is provided to demonstrate options
for using REV\TeX{}4-1 in preparing manuscripts for submission to
JOSA A, JOSA B, \textit{Optics Letters}, and \textit{Applied Optics}. REV\TeX{}4-1 support
for OSA journals was added September 2012 as a BETA and updated in April 2013. Users should obtain the
REV\TeX{}4-1 package (\url{https://authors.aps.org/revtex4/}) and the OSA REV\TeX{}4-1 style files  (on the Author page of any OSA journal site). Authors in need of a length estimate because of page charge concerns can use the OSA REV\TeX{}4-1 template. The template will not yield an exact estimate but should provide a good approximation of the length of the page proof. Figures, large tables, and complex display math may still affect the estimate. Note that the two-column format is acceptable for submission and will meet the needs of OSA peer review and production.
\end{abstract}

\ocis{(140.3490) Lasers, distributed-feedback; (060.2420) Fibers, polarization-maintaining; (060.3735) Fiber
Bragg gratings; (060.2370) Fiber optics sensors.}% REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
                          % NOTE: \ocis{} IS ALIASED TO \pacs{} BUT MUST
                          % FORMAT THE TERMS CORRECTLY FOR EACH JOURNAL

\maketitle %% required

\section{Introduction}

The OSA REV\TeX{}4-1 template is designed to assist authors with creating a two-column manuscript that can be submitted to JOSA A, JOSA B, \textit{Optics Letters}, and \textit{Applied Optics} (separate templates are available for other OSA journals, which have not yet migrated to REV\TeX{}).

\begin{itemize}

\itemsep1em

\item See the ``REVTeX 4.1 Author's Guide'' for an overview of REV\TeX{}4-1's features \cite{revtex-au}.

\item See the ``OSA Author Style Guide'' for points on OSA journal style \cite{osastyle}, such as use of OCIS codes.

\end{itemize}

\section{Preparing a REVTeX{} Manuscript for Submission to an OSA Journal}

\begin{enumerate}

\itemsep1em

\item\emph{\textbf{Optics Letters}} \textbf{authors}: Be aware of two major changes for OL papers. Authors now have a firm \textbf{four}-page limit for their papers, and submitted papers must contain a \textbf{fifth} informational page, with complete references.
\item \textbf{Preamble} Use the following preamble to invoke REV\TeX{}4.1 for OSA journals. Use the ``10~pt'' option for JOSA~A, JOSA~B, and OL; use the ``11~pt'' option for \textit{Applied Optics}:

\begin{verbatim}
\documentclass[osajnl,twocolumn,showpacs,
superscriptaddress,10pt]{revtex4-1}
\end{verbatim}

\item \textbf{Citations} in REV\TeX{} use the \texttt{natbib} package. The \texttt{osajnl4-1.rtx} package will enforce appropriate
style for citations callouts: ``$\ldots$ in this study [1,2].''  Use the \verb+\cite{}+ command for all callouts.

\item \textbf{Bib\TeX{}} may be used to create a file containing the references, whose contents
(i.e., contents of .bbl file) can then be pasted into the bibliography section of the .tex file. References must be contained within the .tex file, not a separate Bib\TeX{} file.

\item \textbf{Compress} your .tex manuscript file and all figures (which should be in EPS format, or PDF format if you are using PDFLaTeX) in a ZIP, TAR or TAR-GZIP package. PRISM will process in LaTeX mode by default but will use PDF LaTeX if PDF figure files are detected. Note: TAR or TAR-GZIP is no longer required. All files must be referenced at the root level (e.g., file figure-1.eps, not /myfigs/figure-1.eps).

\item \textbf{Figures and Tables} It is \textit{not} necessary to place figures and tables at the back of the manuscript. Figures and tables should be sized for display as you wish them to appear in the final article. Do not include a separate listing figure captions and table titles.

\end{enumerate}

\section{Sample Equation, Figure, and Table}

\subsection{Equation}
Sample equation. When a two-column equation is needed, use the \verb+\begin{widetext}\end{widetext}+ environment. See the ``REVTeX 4.1 Author's Guide'' \cite{revtex-au}.

\begin{equation}
 \Delta x \Delta p \approx h.
\end{equation}

\subsection{Figure}
Sample figure environment. Use the \verb+graphicsx+ package. For two-column figures, use an asterisk in the figure environment: \verb+\begin{figure*}\end{figure*}+.

%\begin{figure}[h!]
%\centerline{\includegraphics[width=.8\columnwidth]{richardson-f1.eps}}
%\caption{One-column figure set
%with the figure environment.}
%\end{figure}

\begin{figure}[htbp]
%\centerline{\includegraphics[width=.8\columnwidth]{richardson-f1.eps}}
\caption{One-column figure set with the figure environment.}
\end{figure}

\subsection{Table}
Sample table environment. For long tables, see the ``REVTeX 4.1 Author's Guide'' \cite{revtex-au}.

\begin{table}[h!]
  \caption{A simple table}
  \begin{center}
    \begin{tabular}{ccccccccc}
    \hline
    A & B & C & D & E & F & G & H & I\\
    \hline
    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9\\
    10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18\\
    19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27\\
    \hline
    \end{tabular}
  \end{center}
\end{table}

\begin{thebibliography}{99}
%% Do not include separate BibTeX files; if BibTeX is used,
%% paste the output (contents of .bbl file) here.

\bibitem{revtex-au} \url{https://authors.aps.org/revtex4/}.
\bibitem{osastyle} \url{http://www.opticsinfobase.org/submit/style/jrnls_style.cfm}.

\end{thebibliography}

\end{document}

### 2015-05-20 CacadedTunableFilter.tex
Wei Merge

@@
 %\usepackage{osameet2}
+
+%\newcommand{\EDIT}{}
+\usepackage{ulem}
 
@@
 \begin{document}
-\title{Widely Bandwidth-Tunable Broadband Optical Filter on Silicon}
+\title{Ultra-compact, widely bandwidth-tunable filter using cascaded silicon photonic contra-directional couplers}
 %\date{14/10/2014}
@@
 
-Optical filters are essential components for optical communication applications such as wavelength-division multiplexing (WDM), signal processing, and dynamic bandwidth allocation \cite{DynamicBW}.
-These key devices are now needed in integrated photonic systems, in this case, on the silicon-on-insulator platform (SOI), to achieve the same functions as traditional discrete optical components such as diffractive grating spectrometers.
-Silicon photonics allows for CMOS compatible mass fabrication for low cost, high yield, and large-scale on-chip integration. 
-Future high-capacity transmission systems, e.g., applying the super-channel technique, will require a dynamic channel bandwidth allocation over a few hundred gigahertz \cite{jinno2009spectrum}. 
-However, large bandwidth tunability is currently only available in bulky bench-top systems.
-Existing integrated tunable filters, e.g., using microring resonators and MZ interferometers, have relatively small tunable bandwidth (less than 200 GHz)  \cite{ong2013ultra}.
-Also, their free spectral ranges (FSRs) are small, typically less than 10 nm \cite{ong2013ultra}.
+%Next-generation optical transmission systems require dynamic, efficient bandwidth allocation  
+%Bandwidth tunable optical filters are essential components for optical communication applications such as reconfigurable optical wavelength-division multiplexing (WDM), signal processing, and dynamic bandwidth allocation \cite{DynamicBW}.
+%These key devices are now needed in integrated photonic systems, in this case, on the silicon-on-insulator platform (SOI), to achieve the same functions as traditional discrete optical components such as diffractive grating spectrometers.
+Next-generation optical transmission systems applying flexible networking and the super-channel technique will require highly dynamic channel allocation to drastically increase the spectral efficiency and transmission capacity \cite{jinno2009spectrum, geisler2011demonstration}.
+%over a few hundred gigahertz \cite{jinno2009spectrum}. 
+%bandwidth
+Tunable optical filters, reconfigurable in both center wavelength and bandwidth with scalability towards terahertz \cite{geisler2011demonstration}, are essential for these applications.
+Such large bandwidth tunability is currently only available in bulky bench-top systems using diffractive grating spectrometers or liquid crystals.
+Integrated solutions are desired for lower cost and power consumption.
+In particular, silicon photonics  based on the submicron silicon-on-insulator platform allows for CMOS compatible mass fabrication, enabling low cost, high yield, and high-density chip-scale integration.
+Existing solutions for tunable  filters on silicon include devices based on microring resonators \cite{DynamicBW, ong2013ultra} and Mach-Zehnder interferometers (MZIs).
+These devices have relatively small tunable bandwidth (less than 200 GHz) and small free spectral ranges (FSRs) (typically less than 10 nm), not suitable for high-capacity transmission applications.
 

### 2015-05-21 CacadedTunableFilter.tex
Wav inset

@@
 \includegraphics[width=.99\columnwidth]{data/Passive6}
-\caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz.}
+\caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz.
+Inset shows the filter shape up to -20 dB, which is typical in communications.}
 \label{fig:passive}
@@
 \centering
-\includegraphics[width=.99\columnwidth]{data/Central}
+\includegraphics[width=.99\columnwidth]{data/Central2}
 \caption{Spectral response with the heat applied to both contra-DCs: the central wavelength is tuned from 1535 nm to 1539 nm continuously; the temperatures are calculated by comparison to simulation.}

### 2015-05-21 CacadedTunableFilter.tex
Update

@@
 Our simulations uses  steps of constant length $z_i-z_{i-1}=z_c$. 
-The total response of a contra-DC $C(z_0,z_n)$ is calculated using the transfer-matrix method, where $E(z_0)=C(z_0,z_n) E(z_n)$.
+%The total response of a contra-DC $C(z_0,z_n)$ is calculated using the transfer-matrix method, where $E(z_0)=C(z_0,z_n) E(z_n)$.
 
-\begin{equation}
-\label{eq:CMatrix}
- C(z_0,z_n) =  \prod_{i=1}^{n}\me^{S_{1,i}(z_i-z_{i-1})}\me^{S_{2,i}(z_i-z_{i-1})}
-\end{equation}
+%\begin{equation}
+%\label{eq:CMatrix}
+% C(z_0,z_n) =  \prod_{i=1}^{n}\me^{S_{1,i}(z_i-z_{i-1})}\me^{S_{2,i}(z_i-z_{i-1})}
+%\end{equation}
 
@@
 On top of each contra-DC sits a metal strip acting as a microheater for thermal tuning.  
-The refractive index of silicon has a temperature dependence of 1.87$\times10^{-4}$K$^{-1}$ at room temperature for wavelengths around 1550 nm~\cite{frey2006temperature}.
+The refractive index of silicon has a temperature dependence of $\frac{\diff{n_\text{Si}}}{\diff{T}}=$ 1.87$\times10^{-4}$K$^{-1}$ at room temperature for wavelengths around 1550 nm~\cite{frey2006temperature}.
 Without electrical input, the optical responses of the two filters are identical (neglecting fabrication uniformities) resulting in a sharp transition from the pass-band to the stop-band. 
 Applying independent electrical currents on the heaters, we can shift the spectra of the contra-DCs simultaneously or differentially for wavelength or bandwidth tuning.
-In the ideal case, each contra-DC should be uniformly heated so that the apodization profile does not change as the temperature varies.
+In the ideal case, each contra-DC should be uniformly heated so that the apodization profile isn't disturbed as the temperature varies.
+
+In simulation, the temperature dependence is accounted for by increasing the effective index according to 
+$\diff{n_\text{eff}}=\frac{\diff{n_\text{Si}}}{\diff{T}}*\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}*\diff{T}$, where $\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}$ is calculated using an eigenmode solver.
 
@@
 \caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz.
-Inset shows the filter shape up to -20 dB, which is typical in communications.}
+Inset shows the filter shape up to -20 dB, which is the typical communication requirement.}
 \label{fig:passive}
@@
 \includegraphics[width=.99\columnwidth]{data/Band6}
-\caption{Spectral response of the device for different temperatures applied to only one contra-DC: 1-dB BW tuned down to 65 GHz, 3-dB BW to 117 GHz. The temperatures are obtained from simulation fit.}
+\caption{Spectral response of the device for different temperatures applied to only one contra-DC: 1-dB BW tuned down to 65 GHz, 3-dB BW to 117 GHz.
+The temperatures are obtained from simulation fit.
+Inset shows the temperature dependence.}
 \label{fig:bandTune}
@@
 \includegraphics[width=.99\columnwidth]{data/Central2}
-\caption{Spectral response with the heat applied to both contra-DCs: the central wavelength is tuned from 1535 nm to 1539 nm continuously; the temperatures are calculated by comparison to simulation.}
+\caption{Spectral response with the heat applied to both contra-DCs: the central wavelength is tuned from 1535 nm to 1539 nm continuously; the temperatures are calculated by comparison to simulation.
+Inset shows the temperature dependence.}
 \label{fig:wavTune}

### 2015-05-21 data/rawData/dataFromFigure.m

@@ -32,7 +32,7 @@ normX=xdata; normY=ydata;
 close gcf;
 
 
-open('BestTuningEver.fig');
+open('Filter2Dual.fig');
 % open('Filter2DUAL.fig');
 
 h = gcf; %current figure handle   

### 2015-06-11 CacadedTunableFilter.tex
Abstract

@@
 \begin{abstract}
-We demonstrate an integrated silicon tunable band-pass filter with low in-band ripples of 0.3 dB, a high contrast of 55 dB, and no free-spectral range. 
-A record bandwidth tuning from 788 to 117 GHz was achieved.
+%We demonstrate an integrated silicon tunable band-pass filter with low in-band ripples of 0.3 dB, a high contrast of 55 dB, and no free-spectral range. 
+%A record bandwidth tuning from 788 to 117 GHz was achieved.
+
+We demonstrate an integrated tunable band-pass filter continuously tuned from 788 GHz down to 117 GHz of 3 dB bandwidth with up to 3 nm of wavelength tunability at 1550 nm.
+The out of band contrast is up to 55 dB, the in band ripples are under 0.3 dB and the free spectral range is unlimited.
+This result was achieved using contra-directional couplers and micro-heaters on the silicon-on-insulator platform with a footprint of less than 0.007 mm$^2$.
 \end{abstract}
@@
 Integrated solutions are desired for lower cost and power consumption.
-In particular, silicon photonics  based on the submicron silicon-on-insulator platform allows for CMOS compatible mass fabrication, enabling low cost, high yield, and high-density chip-scale integration.
+In particular, silicon photonics  based on the sub-micron silicon-on-insulator platform allows for CMOS compatible mass fabrication, enabling low cost, high yield, and high-density chip-scale integration.
 Existing solutions for tunable  filters on silicon include devices based on microring resonators \cite{DynamicBW, ong2013ultra} and Mach-Zehnder interferometers (MZIs).
@@
 Analogous to waveguide Bragg gratings, the wavelength selectivity in contra-DCs are based on periodic dielectric perturbations.
-But instead of backreflections in the same waveguide, the selected wavelength in a contra-DC is dropped to another waveguide through contra-directional coupling.
+But instead of back-reflections in the same waveguide, the selected wavelength in a contra-DC is dropped to another waveguide through contra-directional coupling.
 This allows add-drop operation without the need of a circulator. 
@@
 
-On top of each contra-DC sits a metal strip acting as a microheater for thermal tuning.  
+On top of each contra-DC sits a metal strip acting as a micro-heater for thermal tuning.  
 The refractive index of silicon has a temperature dependence of $\frac{\diff{n_\text{Si}}}{\diff{T}}=$ 1.87$\times10^{-4}$K$^{-1}$ at room temperature for wavelengths around 1550 nm~\cite{frey2006temperature}.
@@
 $\diff{n_\text{eff}}=\frac{\diff{n_\text{Si}}}{\diff{T}}*\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}*\diff{T}$, where $\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}$ is calculated using an eigenmode solver.
+
+While only coupling apodization has been discussed so far, it is common in Bragg grating profiles to also adjust the local Bragg wavelength.
+This is done with a phase shift changing the local effective index or period.
+This design only uses coupling apodization in principle, but phase noise also appears during fabrication due to non-uniformity and sidewall roughness.
+There are 3 main types of noise: high frequency (typically around 10 $\mu m$m\cite{simard2013characterization}), which is caused by sidewall roughness, decreases the sidelobe suppression; low frequency (larger than the device or 300 $\mu$m), which is caused by wafer thickness and etching variance, causes a linear chirp that increases the bandwidth; and coupling dependent, which is due to an index difference between low coupling and high coupling regions.
+
+It is possible to easily add high frequency phase noise to the transfer matrix solution by adding random noise to the $\Delta\hat{\beta}$ propagation constants.
+The frequency distribution of the noise will thus match the quantization steps of the matrices, but since the response noise is dependent of both the amplitude and frequency of the sidewall roughness \cite{simard2011impact},we can match the simulation to the experiment by choosing the right noise amplitude.
+Similarly, we can also add a variation to $\Delta\hat{\beta}$ which is dependent on the longitudinal position and the local coupling does not change as the temperature varies.
 
@@
 The power efficiency of the bandwidth tuning is about 24 mW/nm, which can significantly improved by optimizing the heater design, e.g., using smaller heater features and thermal isolation \cite{dong2010thermally}.
+
+We observe that the central wavelength at higher temperature is out of the original band, indicating thermal coupling between the two filters.
+Also, the side-lobes suppression ratio is lower for smaller bandwidth due to the signal only being affected by one filter.
+To solve both of these problems, next generation devices should use a isolation or larger spacing between filter elements (we used 12 \text{$\mu$}m center to center) and additional filtering stages.
 
@@
 
+Table \ref{table:comparison} shows a comparison of this filter with other recent publications of tunable filters.
+No other tunable filter has such a large available bandwidth and FSR, making contra-DC unique in their application potential.
+
 %\section{Conclusion}
 In summary, we have demonstrated a bandwidth tunable filter with a low insertion loss of less then 0.5 dB, low ripples of less than 0.3 dB, a large maximal bandwidth of greater than 750 GHz, and high contrast of 55 dB.
-Compared to other devices based on microring resonators and MZIs (see Table \ref{table:comparison}), it enables a much larger maximal passband and does not suffer from small FSRs. 
 A large bandwidth tuning range over 670 GHz has been achieved, which, to the best of our knowledge, is the widest ever demonstrated on a silicon chip. 
@@
     % \\
-    Ding (2011) &	MRs + MZI &	55 GHz / 1 THz &	28-55 GHz &	3.6 dB &	30 dB
+    Ding (2011)\cite{ding2011bandwidth} &	MRs + MZI &	55 GHz / 1 THz &	28-55 GHz &	3.6 dB &	30 dB
      \\
- 	Orlandi (2012) &	MRs + MZI &	173 GHz / 200 GHz &	23-173 GHz &	0.46-1.06 dB &	15-34 dB
+ 	Orlandi (2012)\cite{orlandi2012reconfigurable} &	MRs + MZI &	173 GHz / 200 GHz &	23-173 GHz &	0.46-1.06 dB &	15-34 dB
       \\

### 2015-08-11 CacadedTunableFilter.tex
figures
text clean up

@@
 
-We demonstrate an integrated tunable band-pass filter continuously tuned from 788 GHz down to 117 GHz of 3 dB bandwidth with up to 3 nm of wavelength tunability at 1550 nm.
+We demonstrate an integrated tunable band-pass filter continuously tuned from 788 GHz down to 117 GHz of 3 dB bandwidth with up to 3 nm of central wavelength tunability at 1550 nm.
 The out of band contrast is up to 55 dB, the in band ripples are under 0.3 dB and the free spectral range is unlimited.
@@
 The center wavelength of a contra-DC is determined by the phase-match condition: $\lambda_\text{c} = \Lambda (n_\text{1}+n_\text{2})$, where $\lambda_\text{c}$ is the center wavelength of contra-directional coupling, $\Lambda$ is the grating pitch, and $n_\text{1}$ and $n_\text{2}$ are the effective refractive indices of the first-order and second-order eigenmodes in the coupler.
-Assuming identical filter designs (i.e., same window functions and parameters) of the cascaded contra-DCs, the bandwidth of the finally dropped signal can be tuned by detuning their center wavelengths.
+Assuming identical filter designs (i.e., same window functions and parameters) of the cascaded contra-DCs, the bandwidth of the finally dropped signal can be tuned by detuning their central wavelengths.
 
@@
 The gratings are formed by sidewall corrugations in strip waveguides with a pitch of 312 nm. 
-The spacing between the waveguides varies between 65 and 135 nm with a Gaussian profile as shown in Fig.~\ref{fig:SEM} for efficient sidelobe suppression, for which details can be found in \cite{shi2013siliconCWDM}.
+The spacing between the waveguides varies between 65 and 135 nm to produce a Gaussian coupling profile apodization as shown in Fig.~\ref{fig:SEM} for efficient sidelobe suppression, for which details can be found in \cite{shi2013siliconCWDM}.
 The spectral responses of each contra-DC is calculated using coupled mode theory, following the same procedure as in  \cite{shi2013siliconContraDC}, with three additions: apodization, temperature and noise simulation.
@@
 The first change is thus to modify the transfer matrix of the system to the product of all the grating elements along the propagation axis.
-This calculation ideally takes shape in an infinite sum, but for computation simplicity, we use a finite number of steps with different couplings that still approximates the apodization profile with enough accuracy.
-Our simulations uses  steps of constant length $z_i-z_{i-1}=z_c$. 
+Our simulations use 100 segments to approximate the constantly changing coupling.
+%This calculation ideally takes shape in an infinite sum, but for computation simplicity, we use a finite number of steps with different couplings that still approximates the apodization profile with enough accuracy.
+%Our simulations uses  steps of constant length $z_i-z_{i-1}=z_c$. 
 %The total response of a contra-DC $C(z_0,z_n)$ is calculated using the transfer-matrix method, where $E(z_0)=C(z_0,z_n) E(z_n)$.
@@
 This design only uses coupling apodization in principle, but phase noise also appears during fabrication due to non-uniformity and sidewall roughness.
-There are 3 main types of noise: high frequency (typically around 10 $\mu m$m\cite{simard2013characterization}), which is caused by sidewall roughness, decreases the sidelobe suppression; low frequency (larger than the device or 300 $\mu$m), which is caused by wafer thickness and etching variance, causes a linear chirp that increases the bandwidth; and coupling dependent, which is due to an index difference between low coupling and high coupling regions.
+There are 2 main types of waveguide noise.
+High frequency roughness(typically around 10 $\mu$m of spacial period\cite{simard2013characterization}), which is caused by sidewall roughness and decreases the sidelobe suppression.
+Low frequency variation(larger than the device or 300 $\mu$m), which is caused by wafer thickness and etching variance, causes a linear chirp that increases the bandwidth; and coupling dependent, which is due to an index difference between low coupling and high coupling regions.
 
@@
 \centering
-\includegraphics[width=.99\columnwidth]{data/Passive6}
+\includegraphics[width=.99\columnwidth]{data/Passive61}
 \caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz.
@@
 \centering
-\includegraphics[width=.99\columnwidth]{data/Phase}
+\includegraphics[width=.99\columnwidth]{data/Phase2}
 \caption{ Group delay response of the tunable filter at the drop port. The delay stays within 12 ps between any two points in the band. The out of band results are noisy due to the weak signal.}

### 2015-08-11 OSA-journal-template.tex
TEMPLATE

\documentclass[9pt,twocolumn,twoside]{osajnl}

\journal{ao} % Choose journal (ao, ol, josaa, josab)

\setboolean{shortarticle}{false} % true = letter, false = research article

\title{\LaTeX\ template for preparing an article for submission to OSA journals \emph{Applied Optics}, \emph{Optics Letters}, \emph{JOSA-A} and \emph{JOSA-B}}

\author[1,2,3]{Author One}
\author[2,*]{Author Two}
\author[1]{Author Three}

\affil[1]{Publications Department, OSA-The Optical Society, 2010 Massachusetts Avenue NW, Washington D.C., 20036}
\affil[2]{School of Science, University of Technology, 2000 J St. NW, Washington DC, 20036}
\affil[3]{School of Optics, University of Technology, 2000 J St. NW, Washington DC, 20036}

\affil[*]{Corresponding author: email@my-email.com}

\dates{Compiled \today}

\ociscodes{(140.3490) Lasers, distributed feedback; (060.2420) Fibers, polarization-maintaining;(060.3735) Fiber Bragg gratings.}

\doi{\url{http://dx.doi.org/10.1364/ao.XX.XXXXXX}}

\begin{abstract}
This template can be used to prepare a research article for submission to OSA’s journals \emph{Applied Optics}, \emph{JOSA A}, \emph{JOSA B}, and \emph{Optics Letters}. For \emph{Optics Letters}, you will need to select \texttt{$\setminus$setboolean\{shortarticle\}\{true\}}. Note that this template can be run from your own \TeX\ system or within the cloud-based \href{https://www.overleaf.com}{Overleaf} system (formerly writeLaTeX). For \emph{Optics Letters} select \setboolean{shortarticle}{true} to get a one-column abstract.
\end{abstract}

\setboolean{displaycopyright}{true}

\begin{document}

\maketitle
\thispagestyle{fancy}
\ifthenelse{\boolean{shortarticle}}{\abscontent}{}

\section{Introduction}

This template is designed to assist with creating a two-column research article or letter to submit to \emph{Applied Optics}, \emph{JOSA A}, \emph{JOSA B}, and \emph{Optics Letters}. See the OSA's \href{http://www.opticsinfobase.org/submit/style/}{Style Guide} and \href{http://www.opticsinfobase.org/submit/templates/}{Manuscript Templates} pages for more details.

If you have a question while using this template on \href{https://www.overleaf.com}{Overleaf}, please use the help menu (``?'') on the top bar to search for help or ask us a question using the option in the lower right of the editor.

\section{Examples of Article Components}
\label{sec:examples}

The sections below show examples of different article components.

\section{Figures and Tables}

It is not necessary to place figures and tables at the back of the manuscript. Figures and tables should be sized as they are to appear in the final article. Do not include a separate list of figure captions and table titles.

Figures and Tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.

\subsection{Sample Figure}

Figure \ref{fig:false-color} shows an example figure.

\begin{figure}[htbp]
\centering
\fbox{\includegraphics[width=\linewidth]{sample}}
\caption{False-color image, where each pixel is assigned to one of seven reference spectra.}
\label{fig:false-color}
\end{figure}

\subsection{Sample Table}

Table \ref{tab:shape-functions} shows an example table.

\begin{table}[htbp]
\centering
\caption{\bf Shape Functions for Quadratic Line Elements}
\begin{tabular}{ccc}
\hline
local node & $\{N\}_m$ & $\{\Phi_i\}_m$ $(i=x,y,z)$ \\
\hline
$m = 1$ & $L_1(2L_1-1)$ & $\Phi_{i1}$ \\
$m = 2$ & $L_2(2L_2-1)$ & $\Phi_{i2}$ \\
$m = 3$ & $L_3=4L_1L_2$ & $\Phi_{i3}$ \\
\hline
\end{tabular}
  \label{tab:shape-functions}
\end{table}

\section{Sample Equation}

Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
\begin{equation}
S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i
\label{eq:refname1}
\end{equation}
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.

\section{Sample Algorithm}

Algorithms can be included using the commands as shown in algorithm \ref{alg:euclid}.

\begin{algorithm}
\caption{Euclid’s algorithm}\label{alg:euclid}
\begin{algorithmic}[1]
\Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
\State $r\gets a\bmod b$
\While{$r\not=0$}\Comment{We have the answer if r is 0}
\State $a\gets b$
\State $b\gets r$
\State $r\gets a\bmod b$
\EndWhile\label{euclidendwhile}
\State \textbf{return} $b$\Comment{The gcd is b}
\EndProcedure
\end{algorithmic}
\end{algorithm}

\section{Supplementary Material}

Consult the \href{https://www.osapublishing.org/submit/style/multimedia.cfm}{Author Guidelines for Supplementary Materials in OSA Journals} for details on accepted types of materials and instructions on how to cite them. All materials must be associated with a figure, table, or equation or be referenced in the results section of the manuscript.

2D and 3D image files and video must be labeled “Visualization,” not “Movie,” “Video,” “Figure,” etc. Machine-readable data (for example, csv files) must be labeled  “Data File.”  Number data files and visualizations consecutively, e.g., “Visualization 1, Visualization 2, etc.”. Such items should be mentioned in the text as either “Dataset” or “Code,” as appropriate, and also be cited in the references list. For example, see Dataset 1 (Ref. [1])  and Code 1 (Ref. [2]). Here are two examples:

Sample Dataset Citation

1. T. Ireno and R. Tadaa, "Chemical and mineral compositions of sediments from ODP Site 127-797" (Geological Institute, University of Tokyo, 2009), http://dx.doi.org/10.1594/PANGAEA.726855.

Sample Code Citation

2. Zima Engineering, ZIMA-CAD-Parts: Application for management of CAD files and projects (version 0.5.0-beta1) [software] (2013), http://sourceforge.net/projects/zima-cad-parts/.

\section*{Funding Information}

\textbf{Funding.} National Science Foundation (NSF) (1263236, 0968895, 1102301); The 863 Program (2013AA014402).

\section*{Acknowledgments}

\textbf{Acknowledgment.} Formal funding declarations should not be included in the acknowledgments but in a Funding Information section as shown above. The acknowledgments may contain information that is not related to funding:

The authors thank H. Haase, C. Wiede, and J. Gabler for technical support.

\section*{References}

Note that \emph{Optics Letters} does not include journal article titles or full page ranges in the published article. Only the first page is required. However, a fifth informational-only page containing the full references should be included. The informational page does not count toward the length restriction.

\bigskip
\noindent Add citations manually or use BibTeX. See \cite{Zhang:14}.

% Bibliography
\bibliography{sample}

%Manual citation list
%\begin{thebibliography}{1}
%\bibitem{Zhang:14}
%Y.~Zhang, S.~Qiao, L.~Sun, Q.~W. Shi, W.~Huang, %L.~Li, and Z.~Yang,
 % \enquote{Photoinduced active terahertz metamaterials with nanostructured
  %vanadium dioxide film deposited by sol-gel method,} Opt. Express \textbf{22},
  %11070--11078 (2014).
%\end{thebibliography}

\end{document}

### 2015-08-26 CacadedTunableFilter.tex
up

@@
 
-%\documentclass[letterpaper,10pt]{article}
-\documentclass[osajnl,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1}
-%\usepackage{osameet2}
+\documentclass[9pt,twocolumn,twoside]{osajnl}
 
-%\newcommand{\EDIT}{}
+\journal{ol} % Choose journal (ao, josaa, josab, ol)
+
+\setboolean{shortarticle}{true}
+
 \usepackage{ulem}
-
 \usepackage{amsmath,amssymb}
@@
 
-\usepackage[utf8]{inputenc} %encoding of the input(this text file)
-\usepackage[T1]{fontenc} 	%uses the right font encoding
-\usepackage{lmodern,textcomp}		%makes font work for fontenc
-\usepackage[french,english]{babel} %multiple languages
-\selectlanguage{english}	%can switch to french later using this
 \usepackage{graphicx,epsfig,epstopdf}
-%\usepackage{caption,subcaption}
 
-%\usepackage[numbers]{natbib}
-%\renewcommand{\bibfont}{\footnotesize}
-%\setlength{\bibsep}{2.0pt}
+\title{Ultra-compact, widely bandwidth-tunable filter using cascaded silicon photonic contra-directional couplers}
+
+\author[1]{Jonathan St-Yves}
+\author[1]{Hadi Bahrami}
+\author[1]{Philippe Jean}
+\author[1]{Sophie Larochelle}
+\author[1,*]{Wei Shi}
+\affil[1]{Centre d'optique, photonique et laser (COPL) and Département de génie électrique et génie informatique, Université Laval, 2375 rue de la Terrasse, Québec (Québec), Canada, G1V 0A6}
+\affil[*]{Corresponding author: wei.shi@gel.ulaval.ca}
+
+\dates{Compiled \today}
+
+\ociscodes{ (130.7408) Wavelength filtering devices; (350.2770) Gratings; (130.3120)   Integrated optics devices}
+
+\doi{\url{http://dx.doi.org/10.1364/ao.XX.XXXXXX}}
+
+\begin{abstract}
+We demonstrate an integrated tunable band-pass filter continuously tuned from 788 GHz down to 117 GHz of bandwidth with up to 3 nm of central wavelength tunability in the infrared C-band.
+The out-of-band contrast is up to 55 dB, the in-band ripples are under 0.3 dB and the free spectral range is unlimited.
+This result was achieved using contra-directional couplers and micro-heaters on the silicon-on-insulator platform with a footprint of less than 0.007 mm$^2$.
+An other iteration pushing the tunability from 1 THz to 100 GHz is discussed.
+\end{abstract}
+
+\setboolean{displaycopyright}{true}
 
 \begin{document}
-\title{Ultra-compact, widely bandwidth-tunable filter using cascaded silicon photonic contra-directional couplers}
-%\date{14/10/2014}
-
-\author{Jonathan St-Yves} 
-\author{Hadi Bahrami}
-\author{Philippe Jean}
-\author{Sophie Larochelle}
-\author{Wei Shi}\email{Corresponding author: wei.shi@gel.ulaval.ca}
-\affiliation{Centre d'optique, photonique et laser (COPL) and Département de génie électrique et génie informatique, Université Laval, 2375 rue de la Terrasse, Québec (Québec), Canada, G1V 0A6}
-
-\begin{abstract}
-%We demonstrate an integrated silicon tunable band-pass filter with low in-band ripples of 0.3 dB, a high contrast of 55 dB, and no free-spectral range. 
-%A record bandwidth tuning from 788 to 117 GHz was achieved.
-
-We demonstrate an integrated tunable band-pass filter continuously tuned from 788 GHz down to 117 GHz of 3 dB bandwidth with up to 3 nm of central wavelength tunability at 1550 nm.
-The out of band contrast is up to 55 dB, the in band ripples are under 0.3 dB and the free spectral range is unlimited.
-This result was achieved using contra-directional couplers and micro-heaters on the silicon-on-insulator platform with a footprint of less than 0.007 mm$^2$.
-\end{abstract}
-
-\pacs{ (130.7408) Wavelength filtering devices; (350.2770) Gratings}
-
-%\linespread{0.95}		%Space saving emergency line
-
 \maketitle
+\thispagestyle{fancy}
+\ifthenelse{\boolean{shortarticle}}{\abscontent}{}
 
@@
 
-%Next-generation optical transmission systems require dynamic, efficient bandwidth allocation  
-%Bandwidth tunable optical filters are essential components for optical communication applications such as reconfigurable optical wavelength-division multiplexing (WDM), signal processing, and dynamic bandwidth allocation \cite{DynamicBW}.
-%These key devices are now needed in integrated photonic systems, in this case, on the silicon-on-insulator platform (SOI), to achieve the same functions as traditional discrete optical components such as diffractive grating spectrometers.
 Next-generation optical transmission systems applying flexible networking and the super-channel technique will require highly dynamic channel allocation to drastically increase the spectral efficiency and transmission capacity \cite{jinno2009spectrum, geisler2011demonstration}.
-%over a few hundred gigahertz \cite{jinno2009spectrum}. 
-%bandwidth
 Tunable optical filters, reconfigurable in both center wavelength and bandwidth with scalability towards terahertz \cite{geisler2011demonstration}, are essential for these applications.
@@
 Existing solutions for tunable  filters on silicon include devices based on microring resonators \cite{DynamicBW, ong2013ultra} and Mach-Zehnder interferometers (MZIs).
-These devices have relatively small tunable bandwidth (less than 200 GHz) and small free spectral ranges (FSRs) (typically less than 10 nm), not suitable for high-capacity transmission applications.
+These devices have relatively small tunable bandwidth (less than 200 GHz) and small free spectral range (FSR) (typically less than 10 nm), not suitable for high-capacity transmission applications.
 
 Contra-directional couplers(contra-DCs) are grating-assisted add-drop filters \cite{shi2013siliconContraDC}. 
-Analogous to waveguide Bragg gratings, the wavelength selectivity in contra-DCs are based on periodic dielectric perturbations.
+Analogous to waveguide Bragg gratings, the wavelength selectivity in contra-DCs is based on periodic dielectric perturbations.
 But instead of back-reflections in the same waveguide, the selected wavelength in a contra-DC is dropped to another waveguide through contra-directional coupling.
@@
 The schematic of the proposed device is shown in Fig.~\ref{fig:schematic}. 
-It consists of a pair of cascaded contra-DCs, each operating as an add-drop filter. 
+It consists of a pair of cascaded contra-DCs, each operating as a drop filter. 
 The drop port of the first contra-DC is connected to the input port of the second contra-DC. 
 Therefore, the finally dropped signal is determined by the product of the  drop-port transfer functions of the two contra-DCs.
+
 The center wavelength of a contra-DC is determined by the phase-match condition: $\lambda_\text{c} = \Lambda (n_\text{1}+n_\text{2})$, where $\lambda_\text{c}$ is the center wavelength of contra-directional coupling, $\Lambda$ is the grating pitch, and $n_\text{1}$ and $n_\text{2}$ are the effective refractive indices of the first-order and second-order eigenmodes in the coupler.
-Assuming identical filter designs (i.e., same window functions and parameters) of the cascaded contra-DCs, the bandwidth of the finally dropped signal can be tuned by detuning their central wavelengths.
+At first, the two filters are identical and drop a large well defined window.
+By changing the temperature of a single filter, the bandwidth of the finally dropped signal can be adjusted by detuning their central wavelengths.
 
@@
 In each contra-DC, the widths of the waveguides are of 560 and 440 nm.
-This high asymmetry ensures a negligible forward coupling. 
+This high asymmetry ensures a negligible forward cross-coupling. 
 The gratings are formed by sidewall corrugations in strip waveguides with a pitch of 312 nm. 
 The spacing between the waveguides varies between 65 and 135 nm to produce a Gaussian coupling profile apodization as shown in Fig.~\ref{fig:SEM} for efficient sidelobe suppression, for which details can be found in \cite{shi2013siliconCWDM}.
+
 The spectral responses of each contra-DC is calculated using coupled mode theory, following the same procedure as in  \cite{shi2013siliconContraDC}, with three additions: apodization, temperature and noise simulation.
-
-%The first part in predicting the contra-directional coupler spectrum is to compute the dielectric variation caused by the perturbation $\Delta\varepsilon(x,y)$ which is $\varepsilon_0/\pi*(n_{max}(x,y)^2-n_{min}(x,y)^2)$ where the $1/\pi$ factor is the first Fourier expansion coefficient in the case of a square shaped perturbation.
-%One also needs the mode distribution in each waveguide  $E_1(x,y)$ and $E_2(x,y)$ at the average point of the perturbation, which can be obtained using a 2D eigenmode solver such as Lumerical MODE. 
-%The couplings $\kappa_{11}$, $\kappa_{12}$ and $\kappa_{22}$  can then be calculated from
-%\begin{equation}\label{eq:coupling}
-%\kappa_{nm}=\frac{\omega}{4}\iint \textbf{E}^*_n(x,y)\Delta\varepsilon_1(x,y) \textbf{E}_m(x,y) \diff x \diff y
-%\end{equation}
 
@@
 Our simulations use 100 segments to approximate the constantly changing coupling.
-%This calculation ideally takes shape in an infinite sum, but for computation simplicity, we use a finite number of steps with different couplings that still approximates the apodization profile with enough accuracy.
-%Our simulations uses  steps of constant length $z_i-z_{i-1}=z_c$. 
-%The total response of a contra-DC $C(z_0,z_n)$ is calculated using the transfer-matrix method, where $E(z_0)=C(z_0,z_n) E(z_n)$.
-
-%\begin{equation}
-%\label{eq:CMatrix}
-% C(z_0,z_n) =  \prod_{i=1}^{n}\me^{S_{1,i}(z_i-z_{i-1})}\me^{S_{2,i}(z_i-z_{i-1})}
-%\end{equation}
-
-%with $\Delta\hat{\beta}_{1,2} = \frac{2\pi}{\lambda}n_{\text{eff }1,2}-\frac{\pi}{\Lambda}$ and
-
-%\begin{equation}
-%S_1= \begin{bmatrix}
-%		j\Delta\hat{\beta}_1 & 0 & 0 & 0 \\
-%		0 & j\Delta\hat{\beta}_2 & 0 & 0 \\
-%		0 & 0 & -j\Delta\hat{\beta}_1 & 0 \\
-%		0 & 0 & 0 & -j\Delta\hat{\beta}_2
-%	 \end{bmatrix}
-%\ end{equation}
-
-%\begin{figure*}[tbp]
-%
-%\begin{equation}
-%\begin{split} 
-%S_2= 
-%\begin{bmatrix}
-%-j\Delta\hat{\beta}_1 & 0 & -j\kappa_{11}\me^{j2\Delta\hat{\beta}_1 z_c} & -j\kappa_{12}\me^{j(\Delta\hat{\beta}_1+\Delta\hat{\beta}_2) z_c} \\
-%0 & -j\Delta\hat{\beta}_2 & -j\kappa_{12}\me^{j(\Delta\hat{\beta}_1+\Delta\hat{\beta}_2) z_c} & -j\kappa_{22}\me^{j2\Delta\hat{\beta}_2 z_c} \\
-%j\kappa^*_{11}\me^{-j2\Delta\hat{\beta}_1 z_c} & j\kappa^*_{12}\me^{-j(\Delta\hat{\beta}_1+\Delta\hat{\beta}_2) z_c} & j\Delta\hat{\beta}_1 & 0 \\
-%j\kappa^*_{12}\me^{-j(\Delta\hat{\beta}_1+\Delta\hat{\beta}_2) z_c} & j\kappa^*_{22}\me^{-j2\Delta\hat{\beta}_2 z_c1} & 0 & j\Delta\hat{\beta}_2
-%	 \end{bmatrix}
-%\end{split} 
-%\end{equation}
-%\hrulefill
-%\end{figure*}
-
-It is possible to easily add phase noise to the transfer matrix solution by adding random noise to the $\Delta\hat{\beta}$ propagation constants. 
-The frequency distribution of the noise will thus match the quantization steps of the matrices, but since the response noise is dependent of both the amplitude and frequency of the sidewall roughness \cite{simard2011impact},we can match the simulation to the experiment by choosing the right noise amplitude.
 
@@
 The refractive index of silicon has a temperature dependence of $\frac{\diff{n_\text{Si}}}{\diff{T}}=$ 1.87$\times10^{-4}$K$^{-1}$ at room temperature for wavelengths around 1550 nm~\cite{frey2006temperature}.
-Without electrical input, the optical responses of the two filters are identical (neglecting fabrication uniformities) resulting in a sharp transition from the pass-band to the stop-band. 
+Without electrical input, the optical responses of the two filters are identical (neglecting fabrication uniformness) resulting in a sharp transition from the pass-band to the stop-band. 
 Applying independent electrical currents on the heaters, we can shift the spectra of the contra-DCs simultaneously or differentially for wavelength or bandwidth tuning.
-In the ideal case, each contra-DC should be uniformly heated so that the apodization profile isn't disturbed as the temperature varies.
+Ideally, each contra-DC should be uniformly heated so that the apodization profile isn't disturbed as the temperature varies.
 
 In simulation, the temperature dependence is accounted for by increasing the effective index according to 
-$\diff{n_\text{eff}}=\frac{\diff{n_\text{Si}}}{\diff{T}}*\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}*\diff{T}$, where $\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}$ is calculated using an eigenmode solver.
+$\diff{n_\text{eff}}=\frac{\diff{n_\text{Si}}}{\diff{T}}*\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}*\diff{T}$, where $\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}$ is evaluated using an eigenmode solver.
 
@@
 This design only uses coupling apodization in principle, but phase noise also appears during fabrication due to non-uniformity and sidewall roughness.
+
 There are 2 main types of waveguide noise.
-High frequency roughness(typically around 10 $\mu$m of spacial period\cite{simard2013characterization}), which is caused by sidewall roughness and decreases the sidelobe suppression.
-Low frequency variation(larger than the device or 300 $\mu$m), which is caused by wafer thickness and etching variance, causes a linear chirp that increases the bandwidth; and coupling dependent, which is due to an index difference between low coupling and high coupling regions.
+High frequency roughness(typically around 10 $\mu$m of spacial period\cite{simard2013characterization}) is caused by sidewall roughness and decreases the sidelobe suppression.
+Low frequency variation(larger than the device or 300 $\mu$m) is caused by wafer thickness and etching variance and causes a linear chirp that increases the bandwidth.
 
-It is possible to easily add high frequency phase noise to the transfer matrix solution by adding random noise to the $\Delta\hat{\beta}$ propagation constants.
-The frequency distribution of the noise will thus match the quantization steps of the matrices, but since the response noise is dependent of both the amplitude and frequency of the sidewall roughness \cite{simard2011impact},we can match the simulation to the experiment by choosing the right noise amplitude.
-Similarly, we can also add a variation to $\Delta\hat{\beta}$ which is dependent on the longitudinal position and the local coupling does not change as the temperature varies.
+High frequency phase noise is added to the transfer matrix solution by adding random noise to the $\Delta\hat{\beta}$ propagation constants.
+The frequency distribution of the noise will thus match the quantization steps of the matrices, but since the response noise is dependent of both the amplitude and frequency of the sidewall roughness \cite{simard2011impact},we can fit the simulation to the experiment by choosing the right noise amplitude.
+Similarly, we can also add a variation to $\Delta\hat{\beta}$ which is dependent on the longitudinal position.
 
@@
 \centering
-\includegraphics[width=.99\columnwidth]{data/Passive61}
+\includegraphics[width=.99\columnwidth]{data/Passive62}
 \caption{ Spectral response of the cascaded filters without heating: 1-dB BW is 733 GHz, 3-dB BW is 788 GHz, 10-dB BW is 868 GHz, and 20-dB BW is 990 GHz.
@@
 The smallest bandwidth measured in this case was limited by the maximal power delivered before the metal heaters (300-nm-thick, 2-$\mu$m-wide Al strips) were damaged. 
-A smaller bandwidth below 50 GHz should be feasible if more robust heaters are used.
 The power efficiency of the bandwidth tuning is about 24 mW/nm, which can significantly improved by optimizing the heater design, e.g., using smaller heater features and thermal isolation \cite{dong2010thermally}.
@@
 Also, the side-lobes suppression ratio is lower for smaller bandwidth due to the signal only being affected by one filter.
-To solve both of these problems, next generation devices should use a isolation or larger spacing between filter elements (we used 12 \text{$\mu$}m center to center) and additional filtering stages.
+To solve both of these problems, next generation devices should use a isolation or larger spacing between filter elements (we used 12 \text{$\mu$}m center to center).
 
@@
 \label{fig:bandTune}
+\end{figure} 
+An improvement upon this design is simulated in Fig.~\ref{fig:bandTuneSimu}.
+By using 4 filtering elements instead of 2, and improving the thermal performances to achieve a stable high temperature, it would be possible to tune the bandwidth from over 1 THz down to under 100 GHz while still maintaining a very high out of band contrast of over 20 dB.
+This simulation uses the noise parameters observed in the 2 stage experiment.
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.99\columnwidth]{data/4StageDesignCompiled}
+\caption{Simulation of the spectral response with the heat applied to two out of four cascaded contra-DCs: the bandwidth can be continuously tuned from 1020 GHz to  51GHz.}
+\label{fig:bandTuneSimu}
 \end{figure}
@@
 \end{figure}
-
-%\section{Theoretical Performance Limits}
-
-%\subsection{Out of band rejection ratio}
-%Limited by \textbf{Apodisation} and Phase Noise.
-%A contra-directional coupler spectrum will contain sidelobes corresponding to the Fourier transform of the coupling profile along the propagation axis. 
-%Using a constant coupling is analogous to a rectangular window, causing sidelobes of over -15 dB. 
-%The use of a Blackman–Nuttall or similar high-order gaussian coupling profile theoretically reduces the sidelobes amplitude to under -50 dB, although electron beam grid resolution distorts the profile by forcing discrete coupling values.
-
-%Still, the dominant cause of weak out of band rejection ratio is phase noise due to sidewall roughness\cite{simard2011impact}.
-The random change of waveguide width causes the effective index of the modes to jitter, causing a variation of the Bragg-wavelength.
-
-%Both of these effects are added to our simulation using a transfer matrix method. 
-%First, multiple matrices are used along the propagation length, with couplings corresponding to the apodization profile.
-%Second, the effective index in each of these matrix is randomly varied by an amount corresponding to the roughness amplitude.
-%Since the effect of phase noise is dependent on it's spacial frequency \cite{simard2011impact}, and this frequency is based on the matrix discreteness, the simulation noise is calibrated using measurements data.
-
-%As seen in this experiment however, it is possible to greatly improve the out of band rejection ratio by cascading multiple filters together, which adds up the rejection ratio of each, at the cost of making the device longer
-
-%\subsection{In-band insertion loss}
-%Limited by length and sidewall roughness loss. 
-%The insertion loss in each device at 1550 nm is mainly caused by the material absorption of silicon and scattering loss due to sidewall roughness. 
-%The most important parameter to optimize losses is the length of the device, which is often a trade-off for other figures of merit.
-
-%\subsection{Maximal Bandwidth}
-%Limited by coupling. Can be enhanced with chirp.
-%The bandwidth of the contra-directional coupler is proportional to the coupling between the two waveguides.
-In practice, the coupling is limited by the field overlap of the first two super-modes as well as the amplitude of the perturbation.
-Electron beam fabrication allows us to put the waveguides very close to each other, resulting in a large field overlap
-
-%\subsection{Minimal Bandwidth}
-%Trade-off with length and phase noise.
 
@@
 
-\begin{table*}[t]
+\begin{table*}[thb]
 \caption{Recent results with multi-element on-chip silicon filters}
@@
       \\
-    This work & Cascaded contra-DC &	778 GHz / Unlimited  &	117-778 GHz &	0.5 dB &	55 dB \\
+    \textbf{This experiment }& Cascaded contra-DC &	778 GHz / Unlimited  &	117-778 GHz &	0.5 dB &	55 dB 
+    \\
+    \textbf{4 Stages }& Cascaded contra-DC &	1020 GHz / Unlimited  &	51-1020 GHz &	<1 dB &	>55 dB 
+    \\
 
@@
     \end{table*}
-
-%\subsection{Edge roll-off / Bandwidth effectiveness}
 
@@
 
-\bibliographystyle{osajnl}
 \bibliography{bibli}

### 2015-10-20 ReviewersReply.tex
Reviews

\documentclass[]{article}

%opening
\title{Reply to reviewers}
\author{Jonathan St-Yves}

\begin{document}

\maketitle

\section{Reviewer 1}
The manuscript entitled "Ultra-compact, widely bandwidth-tunable silicon filter with an unlimited free-spectral range" presents experimental results on an integrated tunable optical filter in the C-band. The manuscript highlights some features of the devices such as the wide tunability (670 GHz), a high-rejection (55dB), the small footprint, and a low group delay variation.
The device is based on a cascaded contra-directional coupler structure, and the authors also show how a four-stage cascaded device could improve some of its characteristics, such as an expanded bandwidth.

The article appears relevant to the scope of Optics Letters and to the research community. The quality of the science and the presentation are very high.
My main concern with this manuscript is with the title, since it suggests "unlimited free-spectral range" where the small print limits that range to the C-band. Since this is misleading, I would rather suggest a more discreet approach.
Other than that, here are some questions that, if addressed, might improve the overall quality further:
\begin{itemize}
\item There is some minor inconsistency with the metrics, highlighting a -20dB level requirement (in Figure 3), and then down-grading it to -15dB (in figure 5 - in particular for the +70K curve)

\emph{Reply}

\item Related to the previous point, the shape of the spectral response degrades substantially - beyond acceptable maybe - when the device is pushed to the limit, the performance in this case is arguably consistent with the advertised metrics (top-hat for instance).

\emph{Reply}

\item Power dissipation: The device described in the manuscript appears to require a significant amount of power which could cause problems if integrated with electronics as suggested. This also will potentially affect the performance of a device comprising even more stages - increasing the effect of cross-talk. Please comment on that and include an estimation of the performance limits of such enhanced devices to their integration potential.

\emph{Reply}

\end{itemize}

Finally, here are some cosmetic defects I have encountered:
\begin{itemize}
\item The color scheme in figures 5, 6 and 7 is probably not optimum - I would advise changing the orange to green.

\emph{Reply}

\item The use of millimeters for the footprint instead of micrometers is confusing.

\emph{Reply}

\item A typo on the 1st paragraph of page 3, "then"; should read "than".

\emph{Thank you for the correction.}

\end{itemize}

\section{Reviewer 2:}
This manuscript reports on the design and measurement of a tunable filter, composed of a pair of cascaded contra-directional couplers, on a silicon-photonics platform. The overall work, and especially the presentation, of the authors is to be highly commended. Every step of the design and measurement processes is described in succinct but complete detail. The cited references seem to provide adequate sources for further detail. The device is to be applauded for its simplistic design yet impressive filtering capability and tunability. Although the manuscript surpasses the standards of many of its peers, we hope that the authors consider the comments below to further strengthen their submission.

\begin{itemize}
\item A brief discussion on the geometry and tolerance requirements of individual corrugations would be appreciated. If precise geometry is not as important as control of periodicity, for example, then this device could be more properly “CMOS compatible” in that highly precise (and less manufacturing-friendly) electron beam lithography may not be an absolute necessity.

\item A brief discussion on the coupling coefficients and radiation losses of the contra-directional couplers may be appropriate. We assume that the coefficients play a large role in obtaining the filter shapes present.

\item It is strange that no mention is given of the “through” and “residue” responses (referring to the nomenclature of Fig. 1).

\item Following from the foregoing two points, we notice a 2-dB insertion loss in Fig. 3. Is this a result of radiation loss or large amounts of signal exiting from the “through” and “residue” ports?

\item We encourage the authors to drop the term “ultra-compact” from their title. By the authors’ own admission, the device is at least 312 µm long, with at least several microns of width. These dimensions may be compact in terms of conventional optical filters, but in a silicon platform, which tends to promise large-scale integrability of components, these dimensions are far from compact.
\end{itemize}

We realize that it may be difficult to add the above suggestions due to lack of space. It should be noted, however, that the first two introductory/review paragraphs of the manuscript can be substantially abridged, with details being deferred to the references.

\section{Pre-Production Review}
\begin{itemize}
\item Please upload electronic figure files in TIFF, EPS, or JPEG format

\item For free color figures online-only please submit electronic art files following instructions given at the journal website:

 https://www.osapublishing.org/submit/style/coloronline.cfm

Use these instructions to submit figures that are or grayscale only:

 https://www.osapublishing.org/ol/submit/style/default.cfm

\item When citing a reference you must include publication, title, authors, and page numbers. You may not use "et al" to indicate additional authors.

\item After revision, please make sure that the references are cited in numerical order; renumber references if necessary. Please remove any duplicate references and renumber accordingly.
\end{itemize}

\end{document}

### 2015-10-20 CacadedTunableFilter.tex
Ignore
Reviews

@@
 The device exhibits a high side-lobe suppression ratio (SLSR) of over 40 dB and a high contrast of about 55 dB between the pass-band and the stop-band. 
-The insertion loss is very low, less than 0.5 dB (i.e., 0.25 dB per contra-DC), with small ripples of less then 0.3 dB within the 1-dB passband over 5.8 nm (733~GHz). 
+The insertion loss is very low, less than 0.5 dB (i.e., 0.25 dB per contra-DC), with small ripples of less than 0.3 dB within the 1-dB passband over 5.8 nm (733~GHz). 
 The edge roll-off rate is 19 dB/nm on the left side and 24 dB/nm on the right side.
@@
 An uneven delay can cause distortion during detection of the signal, just like dispersion.
-The simulation and measurements seen in Fig.~\ref{fig:phase} both show a group delay difference of less then 10 ps.
+The simulation and measurements seen in Fig.~\ref{fig:phase} both show a group delay difference of less than 10 ps.
 \begin{figure}[tbp]
@@
 %\section{Conclusion}
-In summary, we have demonstrated a bandwidth tunable filter with a low insertion loss of less then 0.5 dB, low ripples of less than 0.3 dB, a large maximal bandwidth of greater than 750 GHz, and high contrast of 55 dB.
+In summary, we have demonstrated a bandwidth tunable filter with a low insertion loss of less than 0.5 dB, low ripples of less than 0.3 dB, a large maximal bandwidth of greater than 750 GHz, and high contrast of 55 dB.
 A large bandwidth tuning range over 670 GHz has been achieved, which, to the best of our knowledge, is the widest ever demonstrated on a silicon chip. 

### 2015-10-21 ReviewersReply.tex
Made reviewer changes

@@
 \documentclass[]{article}
+\usepackage{textcomp}
+%\usepackage{amsmath,amssymb}
 
-%opening
 \title{Reply to reviewers}
@@
 
-\section{Reviewer 1}
+\section*{Reviewer 1}
 The manuscript entitled "Ultra-compact, widely bandwidth-tunable silicon filter with an unlimited free-spectral range" presents experimental results on an integrated tunable optical filter in the C-band.
@@
 Since this is misleading, I would rather suggest a more discreet approach.
+
+\emph{The free spectral range is in fact unlimited, at least in the band where silicon and silicon oxide is transparent.
+The second order reflection theoretically happens at $\lambda_c/2$, or about 770 nm in this case.
+To clarify what we mean by free spectral range: it is the spacing between two successive dropped optical intensity maxima.}
+
 Other than that, here are some questions that, if addressed, might improve the overall quality further:
@@
 
-\emph{Reply}
+\emph{While -20 dB is the typical standard, -15 dB also has similar practical uses.
+In cases where side-lobes suppression is important, we expect better performance from the 4 staged design of Figure 7.
+Changed the text to make it clearer and not possibly imply that -15 is the standard.}
 
@@
 
-\emph{Reply}
+\emph{As discussed above, the acceptability of the shape depends of the application. Added the 15 dB figure of merit to the comparison table.}
 
@@
 
-\emph{Reply}
+\emph{Our experiment used a very simplistic heater without thermal isolation or any kind of optimization.
+Using techniques such as the ones described in the reference of this section, these would not be issues.
+In principle, we could only dissipate energy through the electrical connections and the optical inputs and outputs, with the rest of the device being suspended in the air and thus thermally isolated.
+Made some changes to the text to better comment on the issue.}
 
@@
 
-\emph{Reply}
+\emph{Agreed, changed to green.}
 
@@
 
-\emph{Reply}
+\emph{Agreed, changed to micrometers squared.}
 
@@
 
+\emph{And lastly, thank you for the comments and the publication recommendation.}
+
 \end{itemize}
 
-\section{Reviewer 2:}
+\section*{Reviewer 2:}
 This manuscript reports on the design and measurement of a tunable filter, composed of a pair of cascaded contra-directional couplers, on a silicon-photonics platform.
@@
 
-\item A brief discussion on the coupling coefficients and radiation losses of the contra-directional couplers may be appropriate.
+\emph{Large coupling coefficients and precise apodization profiles are easier to achieve with this process, although optical lithography able to resolve the required periodicity and gap between waveguides as seen in Fig.~2~a) could be used.
+The corrugations do not need to be square shaped, but must have a large enough amplitude.}
+
+\emph{Our experience with optical lithography shows that the design needs to be biased to account for amplitude distortion, but it is in principle possible to use CMOS compatible process, albeit with an additional iteration to obtain the biasing information.}
+
+\item A brief discussion on the coupling coefficients and \textbf{radiation losses} of the contra-directional couplers may be appropriate.
 We assume that the coefficients play a large role in obtaining the filter shapes present.
+
+\emph{High coupling coefficients are necessary to design short devices with low through port losses and large bandwidth.
+A comparison with the fabricated device versus a larger coupling is illustrated in Fig.
+7.}
 
@@
 
+\emph{We choose to focus on the drop port response in this article. INCLUDE THROUGH PORT IN FIG 3?}
+
 \item Following from the foregoing two points, we notice a 2-dB insertion loss in Fig. 3. Is this a result of radiation loss or large amounts of signal exiting from the “through” and “residue” ports?
+
+\emph{Fig.
+3 shows an insertion loss of 0.5 dB, both in experiments and in simulation.
+This loss is  mainly due to silicon absorption and waveguide radiative losses (0.4 dB).
+The signal exiting from other ports causes about 0.1 dB of losses.}
 
@@
 These dimensions may be compact in terms of conventional optical filters, but in a silicon platform, which tends to promise large-scale integrability of components, these dimensions are far from compact.
+
+\emph{The device ($\approx$ 7000 \textmu m$^2$) is slightly larger than micro-rings ($\approx$ 3500 \textmu m$^2$) and smaller than most MZI designs($\approx$ 600000 \textmu m$^2$) with similar performance.
+TO DISCUSS WITH WEI }
 \end{itemize}
@@
 
-\section{Pre-Production Review}
+\section*{Pre-Production Review}
 \begin{itemize}

### 2015-10-21 CacadedTunableFilter.tex
Made reviewer changes

@@
 \usepackage{amsmath,amssymb}
-\newcommand{\me}{\mathrm{e}}
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
 
@@
 
-\title{Ultra-compact, widely bandwidth-tunable filter using cascaded silicon photonic contra-directional couplers}
+\title{Ultra-compact, widely bandwidth-tunable silicon filter with an unlimited free-spectral range}
 
@@
 \begin{abstract}
-We demonstrate an integrated tunable band-pass filter continuously tuned from 788 GHz down to 117 GHz of bandwidth with up to 3 nm of central wavelength tunability in the infrared C-band.
-The out-of-band contrast is up to 55 dB, the in-band ripples are under 0.3 dB and the free spectral range is unlimited.
-This result was achieved using contra-directional couplers and micro-heaters on the silicon-on-insulator platform with a footprint of less than 0.007 mm$^2$.
-An other iteration pushing the tunability from 1 THz to 100 GHz is discussed.
+Next-generation high-capacity optical networks require flexible allocation of spectrum resources, for which low-cost optical filters with an ultrawide bandwidth tunability beyond hundred GHz are desired.
+We demonstrate an integrated band-pass filter with the bandwidth continuously tuned across 670 GHz (117 GHz to 788 GHz), which, to the best of our knowledge, is the widest tuning span ever demonstrated on a silicon chip.
+The filter also features simultaneous wavelength tuning and an unlimited free spectral range. 
+We measured an out-of-band contrast of up to 55 dB, low in-band ripples of less than 0.3 dB, and in-band group delay variation of less than 8 ps.
+This result was achieved using cascaded Bragg-grating-assisted contra-directional couplers and micro-heaters on the 220-nm silicon-on-insulator platform with a footprint of less than 7000~\textmu m$^2$.
+Another design with the bandwidth continuously tunable from 50 GHz to 1 THz is also presented.
 \end{abstract}
@@
 Existing solutions for tunable  filters on silicon include devices based on microring resonators \cite{DynamicBW, ong2013ultra} and Mach-Zehnder interferometers (MZIs).
-These devices have relatively small tunable bandwidth (less than 200 GHz) and small free spectral range (FSR) (typically less than 10 nm), not suitable for high-capacity transmission applications.
+These devices have relatively small tunable bandwidth (less than 200 GHz) and small free spectral range (FSR) -- typically less than 10 nm, unable to cover the entire C-band, which are not suitable for high-capacity transmission applications.
 
@@
 The drop port of the first contra-DC is connected to the input port of the second contra-DC. 
-Therefore, the finally dropped signal is determined by the product of the  drop-port transfer functions of the two contra-DCs.
+Therefore, the finally dropped signal("Drop port of the system"), is determined by the product of the  drop-port transfer functions of the two contra-DCs.
 
-The center wavelength of a contra-DC is determined by the phase-match condition: $\lambda_\text{c} = \Lambda (n_\text{1}+n_\text{2})$, where $\lambda_\text{c}$ is the center wavelength of contra-directional coupling, $\Lambda$ is the grating pitch, and $n_\text{1}$ and $n_\text{2}$ are the effective refractive indices of the first-order and second-order eigenmodes in the coupler.
-At first, the two filters are identical and drop a large well defined window.
-By changing the temperature of a single filter, the bandwidth of the finally dropped signal can be adjusted by detuning their central wavelengths.
+%The center wavelength of the contra-DC is determined by the phase-match condition: $\lambda_\text{c} = \Lambda (n_\text{1}+n_\text{2})$, where $\Lambda$ is the grating pitch, and $n_\text{1}$ and $n_\text{2}$ are the effective indices of the first-order and second-order eigenmodes in the coupler.
+At first, the two filters are identical and drop a large, well-defined window.
+By changing the temperature of a single filter, the bandwidth of the finally dropped signal can be adjusted by detuning the center wavelengths of the two contra-DCs.
 
@@
 A broadband filter design for a coarse WDM on the 220-nm SOI platform \cite{shi2013siliconCWDM} is adopted for individual contra-DCs.  
-In each contra-DC, the widths of the waveguides are of 560 and 440 nm.
+In each contra-DC, the widths of the waveguides are 560 nm and 440 nm.
 This high asymmetry ensures a negligible forward cross-coupling. 
 The gratings are formed by sidewall corrugations in strip waveguides with a pitch of 312 nm.
-The spacing between the waveguides varies between 65 and 135 nm to produce a Gaussian coupling profile apodization as shown in Fig.~\ref{fig:SEM} for efficient sidelobe suppression, for which details can be found in \cite{shi2013siliconCWDM}.
+Each contra-DC has 1,000 grating elements for a length of 312 \textmu m.
+The spacing between the waveguides varies between 65 and 135 nm to produce a Gaussian-profiled coupling apodization as shown in Fig.~\ref{fig:SEM} for efficient sidelobe suppression, for which details can be found in \cite{shi2013siliconCWDM}.
 
-The spectral responses of each contra-DC is calculated using coupled mode theory, following the same procedure as in  \cite{shi2013siliconContraDC}, with three additions: apodization, temperature and noise simulation.
-
-While an unapodized (uniform) grating can be simulated with only two transfer matrices , $S_1$ and $S_2$ \cite{shi2013siliconContraDC}, an apodized one needs both of these matrices for each step along the propagation, to match the change of coupling.
-The first change is thus to modify the transfer matrix of the system to the product of all the grating elements along the propagation axis.
-Our simulations use 100 segments to approximate the constantly changing coupling.
+The spectral responses of each contra-DC is calculated using coupled mode theory and the transfer matrix method, following the same procedure as in  \cite{shi2013siliconContraDC}, with three additions: apodization, temperature dependence and noise simulation.
+While an unapodized (uniform) grating can be simulated with only two transfer matrices,
+an apodized design needs an independent matrix for each grating element along the propagation, to match the change of coupling, and the transfer matrix of the entire contra-DC is given by the product of all the grating elements along the propagation axis.
+Our simulations use 100 segments to approximate the continuously varied coupling.
 
 On top of each contra-DC sits a metal strip acting as a micro-heater for thermal tuning.  
-The refractive index of silicon has a temperature dependence of $\frac{\diff{n_\text{Si}}}{\diff{T}}=$ 1.87$\times10^{-4}$K$^{-1}$ at room temperature for wavelengths around 1550 nm~\cite{frey2006temperature}.
-Without electrical input, the optical responses of the two filters are identical (neglecting fabrication uniformness) resulting in a sharp transition from the pass-band to the stop-band. 
+The refractive index of silicon has a temperature dependence of 
+${\mathrm{d}{n_\text{Si}}}/{\mathrm{d}T}=$ 1.87$\times10^{-4}$K$^{-1}$
+at room temperature for wavelengths around 1550 nm~\cite{frey2006temperature}.
+Without electrical input, the optical responses of the two filters are in principle identical (except for fabrication errors), resulting in a sharp transition from the pass-band to the stop-band. 
 Applying independent electrical currents on the heaters, we can shift the spectra of the contra-DCs simultaneously or differentially for wavelength or bandwidth tuning.
-Ideally, each contra-DC should be uniformly heated so that the apodization profile isn't disturbed as the temperature varies.
-
-In simulation, the temperature dependence is accounted for by increasing the effective index according to 
-$\diff{n_\text{eff}}=\frac{\diff{n_\text{Si}}}{\diff{T}}*\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}*\diff{T}$, where $\frac{\diff{n_\text{eff}}}{\diff{n_\text{Si}}}$ is evaluated using an eigenmode solver.
+Ideally, each contra-DC should be uniformly heated so that the apodization profile would not be disturbed as the temperature varies.
+In simulation, the temperature dependence is accounted for by 
+$\mathrm{d}n_\text{eff}=\mathrm{d}n_\text{Si}/{\mathrm{d}T}\times\mathrm{d}n_\text{eff}/{\mathrm{d}n_\text{Si}}\times\mathrm{d}T$, where $\mathrm{d}n_\text{eff}/{\mathrm{d}n_\text{Si}}$ is evaluated using an eigenmode solver.
 
 While only coupling apodization has been discussed so far, it is common in Bragg grating profiles to also adjust the local Bragg wavelength.
-This is done with a phase shift changing the local effective index or period.
+This can be done with a phase shift changing the local effective index or period.
 This design only uses coupling apodization in principle, but phase noise also appears during fabrication due to non-uniformity and sidewall roughness.
 
-There are 2 main types of waveguide noise.
-High frequency roughness(typically around 10 $\mu$m of spacial period\cite{simard2013characterization}) is caused by sidewall roughness and decreases the sidelobe suppression.
-Low frequency variation(larger than the device or 300 $\mu$m) is caused by wafer thickness and etching variance and causes a linear chirp that increases the bandwidth.
-
-High frequency phase noise is added to the transfer matrix solution by adding random noise to the $\Delta\hat{\beta}$ propagation constants.
-The frequency distribution of the noise will thus match the quantization steps of the matrices, but since the response noise is dependent of both the amplitude and frequency of the sidewall roughness \cite{simard2011impact},we can fit the simulation to the experiment by choosing the right noise amplitude.
+There are two main types of waveguide noise considered in our simulation.
+High-frequency phase noise (typically around 10 \textmu m of spacial period \cite{simard2013characterization}) is caused by sidewall roughness and decreases the sidelobe suppression.
+Low-frequency phase noise, with a correlation length larger than the device (300 \textmu m), is caused by the wafer thickness non-uniformity and etching variance, resulting in a linear chirp that increases the bandwidth.
+High frequency phase noise is considered in our simulation by adding random noise $\Delta\hat{\beta}$ to the propagation constants.
+The frequency distribution of the noise thus matches the quantization steps of the matrices, but since the response noise is dependent on both the amplitude and frequency of the sidewall roughness \cite{simard2011impact}, we can fit the simulation to the experiment by choosing the right noise amplitude.
 Similarly, we can also add a variation to $\Delta\hat{\beta}$ which is dependent on the longitudinal position.
@@
 The device was fabricated using a CMOS-compatible technology with electron-beam lithography. 
-Fiber grating couplers\cite{zhong2014focusingFGC} were used as optical IOs in the measurement. 
+Large coupling coefficients and precise apodization profiles are easier to achieve with this process, although optical lithography able to resolve the required periodicity and gap between waveguides as seen in \ref{fig:SEM} a) could be used.
+The corrugations do not need to be square shaped, but must have a large enough amplitude
+.
+Fiber grating couplers \cite{zhong2014focusingFGC} are used as optical inputs and outputs in the measurement. 
 Fig.~\ref{fig:passive} shows the measured drop port response of the cascaded contra-DC filters. 
@@
 The edge roll-off rate is 19 dB/nm on the left side and 24 dB/nm on the right side.
-Further work could optimize the grating structure using the inverse layer peeling algorithm\cite{skaar2001synthesis} since the mathematics of the contra-directional coupler are similar to those of Bragg gratings.
+The simulation agrees well with experiment.
 
-By changing the temperature of a single contra-DC, we offset the phase-match condition of a filter, resulting in a smaller band overlap between the two contra-DCs and thus a narrower passband in the drop port, as shown in Fig.~\ref{fig:bandTune}.
-Due to the wavelength detuning,  the stop-band edges are only determined by the single filters. 
-As a result, the side-lobes suppression degrades  for small bandwidths but is still better than 15 dB.
+%\subsection{Phase}
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=.99\columnwidth]{data/Phase3}
+\caption{ Group delay response of the tunable filter at the drop port. The delay stays within 8 ps between any two points in the band. The out of band results are noisy due to the weak signal.}
+\label{fig:phase}
+\end{figure}
+Another important parameter to monitor is the group delay, as an uneven delay within the pass band may cause signal distortion.
+The simulation and measurements seen in Fig.~\ref{fig:phase} both show a group delay difference of less than 8~ps within the 1-dB bandwidth.
+Compared to the original design without considering the phase noise due to fabrication errors, the measured group delay shows a slight distortion.
+Good agreement is obtained by taking into consideration the linear chirp caused by the silicon wafer thickness variation.
+
+Further work could optimize the grating structure further using the inverse layer peeling algorithm\cite{skaar2001synthesis} since the mathematics of the contra-directional coupler are similar to those of Bragg gratings.
+
+By changing the temperature of a single contra-DC, we shift its phase-match condition, resulting in a smaller band overlap between the two contra-DCs and thus a narrower passband in the drop port, as shown in Fig.~\ref{fig:bandTune}.
+Due to the wavelength detuning,  the stop-band edges are now determined by the single filters. 
+As a result, the side-lobes suppression for small bandwidths degrades to -15 dB.
 A continuous tuning of the 3-dB bandwidth from 788 GHz down to 117 GHz (i.e., over 670 GHz or 5.4 nm) is experimentally observed as the on-chip temperature increases by 70 degrees.
-The smallest bandwidth measured in this case was limited by the maximal power delivered before the metal heaters (300-nm-thick, 2-$\mu$m-wide Al strips) were damaged. 
-The power efficiency of the bandwidth tuning is about 24 mW/nm, which can significantly improved by optimizing the heater design, e.g., using smaller heater features and thermal isolation \cite{dong2010thermally}.
 
-We observe that the central wavelength at higher temperature is out of the original band, indicating thermal coupling between the two filters.
-Also, the side-lobes suppression ratio is lower for smaller bandwidth due to the signal only being affected by one filter.
-To solve both of these problems, next generation devices should use a isolation or larger spacing between filter elements (we used 12 \text{$\mu$}m center to center).
+The microheaters are made of 300-nm-thick, 2-\textmu m-wide Al strips.
+The power efficiency of the bandwidth tuning is about 24~mW/nm, which dissipates a lot of heat and would be impractical for integration with electronics.
+We also observe a slight red-shift of the center wavelength at higher temperature, indicating thermal coupling between the two contra-DCs that are about 10 \textmu m away from each other.
+These issues can be resolved by optimizing the heater design, e.g., using smaller heater features and thermal isolation \cite{dong2010thermally}.
 
@@
 \end{figure}
-An improvement upon this design is simulated in Fig.~\ref{fig:bandTuneSimu}.
-By using 4 filtering elements instead of 2, and improving the thermal performances to achieve a stable high temperature, it would be possible to tune the bandwidth from over 1 THz down to under 100 GHz while still maintaining a very high out of band contrast of over 20 dB.
-This simulation uses the noise parameters observed in the 2 stage experiment.
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.99\columnwidth]{data/4StageDesignCompiled}
-\caption{Simulation of the spectral response with the heat applied to two out of four cascaded contra-DCs: the bandwidth can be continuously tuned from 1020 GHz to  51GHz.}
-\label{fig:bandTuneSimu}
-\end{figure}
 
@@
 As shown in Fig.~\ref{fig:wavTune}, when the center wavelength is continually changed over 4 nm by varying the on-chip temperature, the filter shape is maintained with sharp edges. 
-Actually, slight detuning between the cascaded contra-DCs may be used to compensate for band-edge distortions due to fabrication errors for a more symmetric filter shape.
-The power efficiency of the wavelength tuning is about 44 mW/nm, which is about twice the power consumption of the bandwidth tuning since two contra-DCs are heated simultaneously.
+%Actually, slight detuning between the cascaded contra-DCs may be used to compensate for band-edge distortions due to fabrication errors for a more symmetric filter shape. 
+The power efficiency of the wavelength tuning is about 44~mW/nm, which is about twice the power consumption of the bandwidth tuning since two contra-DCs are heated simultaneously.
 \begin{figure}[htbp]
@@
 
-%\subsection{Phase/dispertion}
-An other important parameter to monitor is the group delay of the device.
-An uneven delay can cause distortion during detection of the signal, just like dispersion.
-The simulation and measurements seen in Fig.~\ref{fig:phase} both show a group delay difference of less than 10 ps.
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=.99\columnwidth]{data/Phase2}
-\caption{ Group delay response of the tunable filter at the drop port. The delay stays within 12 ps between any two points in the band. The out of band results are noisy due to the weak signal.}
-\label{fig:phase}
-\end{figure}
-
-Table \ref{table:comparison} shows a comparison of this filter with other recent publications of tunable filters.
-No other tunable filter has such a large available bandwidth and FSR, making contra-DC unique in their application potential.
-
-%\section{Conclusion}
-In summary, we have demonstrated a bandwidth tunable filter with a low insertion loss of less than 0.5 dB, low ripples of less than 0.3 dB, a large maximal bandwidth of greater than 750 GHz, and high contrast of 55 dB.
-A large bandwidth tuning range over 670 GHz has been achieved, which, to the best of our knowledge, is the widest ever demonstrated on a silicon chip. 
-This ultra-wide bandwidth tunability makes the device very attractive for next-generation ultrahigh baud-rate applications (e.g., high-capacity super-channel transmissions) and flexible optical networking.
-
 \begin{table*}[thb]
@@
 \hline
-	Publication & Filter type & BWmax / FSR & Tunable BW & On-chip loss & Contrast \\
+Publication & Filter type & BWmax / FSR & Tunable BW & On-chip loss / Ripples & Contrast \\
 \hline
-    %Ibrahim (2011) &	Cascaded MRs &	0.4 GHz / 10 GHz &	0.6-2 GHz &	0.6 dB &	30 dB
-    % \\
-    %Alipour (2011) &	Cascaded MRs &	5 GHz / 650 Ghz &	0.8-5 GHz &	1.25-3.75 dB &	38 dB
-    % \\
-    Ding (2011)\cite{ding2011bandwidth} &	MRs + MZI &	55 GHz / 1 THz &	28-55 GHz &	3.6 dB &	30 dB
+Ding (2011)\cite{ding2011bandwidth} &	MRs + MZI &	55 GHz / 1 THz &	28-55 GHz &	3.6 dB / 1 dB &	30 dB
 \\
- 	Orlandi (2012)\cite{orlandi2012reconfigurable} &	MRs + MZI &	173 GHz / 200 GHz &	23-173 GHz &	0.46-1.06 dB &	15-34 dB
+Orlandi (2012)\cite{orlandi2012reconfigurable} &	MRs + MZI &	173 GHz / 200 GHz &	23-173 GHz &	0.46-1.06 dB / 0.5 dB &	15-34 dB
 \\
-    %Luo (2012) &	Cascaded MRs &	100 GHz / 750 Ghz &	No &	0.3-0.6 dB &	50 dB  \\
-    Ong (2013)\cite{ong2013ultra} &	Cascaded MRs &	125 GHz/ 0.9 THz &	11.6-125 GHz &	0.25 dB &	50-100 dB
+Ong (2013)\cite{ong2013ultra} &	Cascaded MRs &	125 GHz/ 0.9 THz &	11.6-125 GHz &	0.25 dB / 3 dB &	50-100 dB
 \\
-    \textbf{This experiment }& Cascaded contra-DC &	778 GHz / Unlimited  &	117-778 GHz &	0.5 dB &	55 dB 
+\textbf{This experiment }& Cascaded contra-DC &	778 GHz / Unlimited  &	67-778 GHz &	0.5 dB / 0.3 dB &	15-55 dB 
 \\
-    \textbf{4 Stages }& Cascaded contra-DC &	1020 GHz / Unlimited  &	51-1020 GHz &	<1 dB &	>55 dB 
+\textbf{4-stage design  }& Cascaded contra-DC &	1 THz / Unlimited  &	49-1007 GHz &	<1 dB / 0.3 dB & >49 dB 
 \\
@@
 
+Table \ref{table:comparison} shows a comparison of recent publications of tunable optical filters on the SOI platform. 
+Our device shows the highest tunable bandwidth and is the only one that allows for a bandwidth beyond 200~GHz. 
+It is noteworthy that the other devices all have a small FSR less than the span of the C-band (35~nm), while our device does not suffer from a limited FSR.
+This indicates a unique capacity for dynamic allocation of spectrum resources.
+In addition, our device is among the best in terms of loss ripples and contrast.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.99\columnwidth]{data/4StageDesignCompiled2}
+\caption{Simulation of the spectral response with the heat applied to two out of four cascaded contra-DCs: the 1 dB bandwidth can be continuously tuned from 1007 GHz to  49GHz.
+The sidelobes stay under -49 dB even for small bandwidths due to the double filtering.
+This simulation doesn't consider fabrication phase noise.}
+\label{fig:bandTuneSimu}
+\end{figure}
+
+For improved performance and flexibility, more stages can be cascaded.
+Fig.~\ref{fig:bandTuneSimu} shows our simulation results of a 4-stage cascade contra-DC filter, consisting of two pairs of identical contra-DCs with a stronger coupling than the one experimentally demonstrated (53500~m$^{-1}$ vs 38000~m$^{-1}$).
+Each pair is controlled by the same temperature, performing as a single tuning element.
+
+%\section{Conclusion}
+In summary, we have demonstrated a bandwidth tunable filter with a low insertion loss of less than~0.5 dB, low ripples of less than~0.3 dB, a large maximal bandwidth of greater than 750~GHz, and high contrast of 55~dB.
+A large bandwidth tuning range over 670~GHz has been achieved, which, to the best of our knowledge, is the widest ever demonstrated on a silicon chip. 
+This ultra-wide bandwidth tunability makes the device very attractive for next-generation ultrahigh baud-rate applications (e.g., high-capacity super-channel transmissions) and flexible optical networking.
+
 \section*{Acknowledgments}
 We acknowledge CMC Microsystems for the  software and the fabrication subsidy.
-We thank Yun Wang and Lukas Chrostowski with the Univeristy of British Columbia for the fiber grating coupler design.
-The authors acknowledge the Natural Sciences and Engineering Research Council of Canada, TeraXion and Prompt for funding this research.
+We thank Yun Wang and Lukas Chrostowski with the University of British Columbia for the fiber grating coupler design.
+The authors acknowledge the Natural Sciences and Engineering Research Council of Canada for funding this research.
+This work is part of the SPEED research project (Silicon Photonic Electrically Engineered Devices) funded by NSERC (RDCPJ438811-12), PROMPT (PJT-2011-17), and TeraXion.
 The silicon chip was fabricated at the University of Washington Microfabrication/Nanotechnology User Facility, a member of the NSF National Nanotechnology Infrastructure Network.

### 2015-10-22 ReviewersReply.tex
Update from Wei meeting

@@
 A comparison with the fabricated device versus a larger coupling is illustrated in Fig.
-7.}
+7.
+Comment on losses with the reference \cite{caverley2015measurement}}
 
@@
 
-\emph{The device ($\approx$ 7000 \textmu m$^2$) is slightly larger than micro-rings ($\approx$ 3500 \textmu m$^2$) and smaller than most MZI designs($\approx$ 600000 \textmu m$^2$) with similar performance.
-TO DISCUSS WITH WEI }
+\emph{The device ($\approx$ 7,000 \textmu m$^2$) is about hte same size as micro-rings ( also $\approx$ 7,000 \textmu m$^2$) and smaller than most MZI designs($\approx$ 600,000 \textmu m$^2$) with similar performance.
+Changed to "Compact" }
 \end{itemize}
@@
 
+\bibliography{bibli}
+\bibliographystyle{osajnl}
+
 \end{document}

### 2015-10-22 CacadedTunableFilter.tex
Update from Wei meeting

@@
 
-\title{Ultra-compact, widely bandwidth-tunable silicon filter with an unlimited free-spectral range}
+\title{Compact and widely bandwidth-tunable silicon filter with an unlimited free-spectral range}
 
@@
 	We measured an out-of-band contrast of up to 55 dB, low in-band ripples of less than 0.3 dB, and in-band group delay variation of less than 8 ps.
-This result was achieved using cascaded Bragg-grating-assisted contra-directional couplers and micro-heaters on the 220-nm silicon-on-insulator platform with a footprint of less than 7000~\textmu m$^2$.
+	This result was achieved using cascaded Bragg-grating-assisted contra-directional couplers and micro-heaters on the 220-nm silicon-on-insulator platform with a footprint of less than 7,000~\textmu m$^2$.
 Another design with the bandwidth continuously tunable from 50 GHz to 1 THz is also presented.
@@
 	For improved performance and flexibility, more stages can be cascaded.
-Fig.~\ref{fig:bandTuneSimu} shows our simulation results of a 4-stage cascade contra-DC filter, consisting of two pairs of identical contra-DCs with a stronger coupling than the one experimentally demonstrated (53500~m$^{-1}$ vs 38000~m$^{-1}$).
+	Fig.~\ref{fig:bandTuneSimu} shows our simulation results of a 4-stage cascade contra-DC filter, consisting of two pairs of identical contra-DCs with a stronger coupling than the one experimentally demonstrated (53.5~mm$^{-1}$ vs 38~mm$^{-1}$).
 Each pair is controlled by the same temperature, performing as a single tuning element.

### 2015-10-22 ReviewersReply.tex
ChangesDocument

--- 2015-10-20 ReviewersReply.tex
@@
-\documentclass[]{article}
+\documentclass[]{letter}
+\usepackage{textcomp}
+\usepackage[margin=1.5in]{geometry}
+%\usepackage{amsmath,amssymb}
 
-%opening
 \title{Reply to reviewers}
-\author{Jonathan St-Yves}
+%\author{Jonathan St-Yves}
 
@@
 
-\maketitle
+%\maketitle
 
-\section{Reviewer 1}
-The manuscript entitled "Ultra-compact, widely bandwidth-tunable silicon filter with an unlimited free-spectral range" presents experimental results on an integrated tunable optical filter in the C-band.
+Dear reviewers,
+
+Thank you for taking the time to review this article and contribute to the discussion to improve it's quality.
+The reviewers raised multiple valid points, and we will address them one by one in this reply.
+Please see the attached document to see the revised article with changes being underlined.
+
+%\section*{Reviewer 1}
+\textbf{Reviewer 1:} The manuscript entitled "Ultra-compact, widely bandwidth-tunable silicon filter with an unlimited free-spectral range" presents experimental results on an integrated tunable optical filter in the C-band.
 The manuscript highlights some features of the devices such as the wide tunability (670 GHz), a high-rejection (55dB), the small footprint, and a low group delay variation.
@@
 Since this is misleading, I would rather suggest a more discreet approach.
-Other than that, here are some questions that, if addressed, might improve the overall quality further:
+
+\textbf{Reply:} The free spectral range is in fact unlimited, at least in the band where silicon and silicon oxide is transparent.
+The second order reflection theoretically happens at $\lambda_c/2$, or about 770 nm in this case.
+To clarify what we mean by free spectral range: it is the spacing between two successive dropped optical intensity maxima. It is not limited to the C-band.
+
+\textbf{Reviewer 1:} Other than that, here are some questions that, if addressed, might improve the overall quality further:
 \begin{itemize}
@@
 
-\emph{Reply}
+\textbf{Reply:} While -20 dB is the typical standard, -15 dB also has similar practical uses.
+In cases where side-lobes suppression is important, we expect better performance from the 4 staged design of Figure 7.
+Changed the text to make it clearer and not possibly imply that -15 is the standard.
 
@@
 
-\emph{Reply}
+\textbf{Reply:} Added the 15 dB figure of merit to the comparison table.
 
@@
 
-\emph{Reply}
+\textbf{Reply:} Our experiment used a very simplistic heater without thermal isolation or any kind of optimization.
+Using techniques such as the ones described in the reference of this section, these would not be issues.
+In principle, we could only dissipate energy through the electrical connections and the optical inputs and outputs, with the rest of the device being suspended in the air and thus thermally isolated.
+Made some changes to the text to better comment on the issue.
 
@@
 
-Finally, here are some cosmetic defects I have encountered:
+\textbf{Reviewer 1:} Finally, here are some cosmetic defects I have encountered:
 \begin{itemize}
@@
 
-\emph{Reply}
+\textbf{Reply:} Agreed, changed to green.
 
@@
 
-\emph{Reply}
+\textbf{Reply:} Agreed, changed to micrometers squared.
 
@@
 
-\emph{Thank you for the correction.}
+\textbf{Reply:} Thank you for the correction.
 
@@
 
-\section{Reviewer 2:}
-This manuscript reports on the design and measurement of a tunable filter, composed of a pair of cascaded contra-directional couplers, on a silicon-photonics platform.
+%\section*{Reviewer 2:}
+\textbf{Reviewer 2:} This manuscript reports on the design and measurement of a tunable filter, composed of a pair of cascaded contra-directional couplers, on a silicon-photonics platform.
 The overall work, and especially the presentation, of the authors is to be highly commended.
@@
 
+\textbf{Reply:} Large coupling coefficients and precise apodization profiles are easier to achieve with this process, although optical lithography able to create the required periodicity and gap between waveguides as seen in Fig.~2~a) could be used.
+The corrugations do not need to be square shaped, but must have a large enough amplitude.
+
+Our experience with optical lithography shows that the design needs to be biased to account for amplitude distortion, but it is in principle possible to use CMOS compatible process, albeit with an additional iteration to obtain the biasing information.
+
 \item A brief discussion on the coupling coefficients and radiation losses of the contra-directional couplers may be appropriate.
@@
 
+\textbf{Reply:} High coupling coefficients are necessary to design short devices with low through port losses and large bandwidth.
+A comparison with the fabricated device versus a larger coupling is illustrated in Fig.
+7.
+We've added a comment on the losses and the reference \textit{Measurement of optical losses in silicon photonic contra-directional couplers}.
+
 \item It is strange that no mention is given of the “through” and “residue” responses (referring to the nomenclature of Fig. 1).
 
+\textbf{Reply:} We choose to focus on the drop port response in this article. We unfortunately do not have the measurements of the other ports for this device.
+
 \item Following from the foregoing two points, we notice a 2-dB insertion loss in Fig. 3. Is this a result of radiation loss or large amounts of signal exiting from the “through” and “residue” ports?
+
+\textbf{Reply:} Fig.
+3 shows an insertion loss of 0.5 dB, both in experiments and in simulation.
+This loss is  mainly due to silicon absorption and waveguide radiative losses (about 0.4 dB).
+The signal exiting from other ports causes less than 0.1 dB of losses.
+We've added a label to better show the insertion loss on the figure.
 
@@
 These dimensions may be compact in terms of conventional optical filters, but in a silicon platform, which tends to promise large-scale integrability of components, these dimensions are far from compact.
+
+\textbf{Reply:} The device ($\approx$ 7,000 \textmu m$^2$) is about the same size as micro-rings ( also $\approx$ 7,000 \textmu m$^2$) and smaller than most MZI designs($\approx$ 600,000 \textmu m$^2$) with similar performance.
+Changed to "Compact".
 \end{itemize}
 
-We realize that it may be difficult to add the above suggestions due to lack of space.
+\textbf{Reviewer 2:} We realize that it may be difficult to add the above suggestions due to lack of space.
 It should be noted, however, that the first two introductory/review paragraphs of the manuscript can be substantially abridged, with details being deferred to the references.
 
-\section{Pre-Production Review}
-\begin{itemize}
-\item Please upload electronic figure files in TIFF, EPS, or JPEG format
+\textbf{Reply:} In order to make space for the additional content, the passage explaining the relationship between the effective indexes, period and central reflected wavelength has been removed, being redundant with the references and not containing critical information for the understanding of this article.
 
-\item For free color figures online-only please submit electronic art files following instructions given at the journal website:
+This concludes the author's reply to the reviewers. Thanks again for all the great comments, which will greatly improve the clarity of the article.
 
- https://www.osapublishing.org/submit/style/coloronline.cfm
+Sincerely,
 
-Use these instructions to submit figures that are or grayscale only:
+The authors of manuscript 249853
 
- https://www.osapublishing.org/ol/submit/style/default.cfm
+%\section*{Pre-Production Review}
+%\begin{itemize}
+%\item Please upload electronic figure files in TIFF, EPS, or JPEG format
 
-\item When citing a reference you must include publication, title, authors, and page numbers. You may not use "et al" to indicate additional authors.
+%\item For free color figures online-only please submit electronic art files following instructions given at the journal website:
 
-\item After revision, please make sure that the references are cited in numerical order; renumber references if necessary. Please remove any duplicate references and renumber accordingly.
-\end{itemize}
+% https://www.osapublishing.org/submit/style/coloronline.cfm
+
+%Use these instructions to submit figures that are or grayscale only:
+
+% https://www.osapublishing.org/ol/submit/style/default.cfm
+
+%\item When citing a reference you must include publication, title, authors, and page numbers. You may not use "et al" to indicate additional authors.
+
+%\item After revision, please make sure that the references are cited in numerical order; renumber references if necessary. Please remove any duplicate references and renumber accordingly.
+%\end{itemize}
+
+%\bibliography{bibli}
+%\bibliographystyle{osajnl}
 

### 2015-10-22 CacadedTunableFilterChanges.tex
ChangesDocument

--- 2015-10-22 CacadedTunableFilter.tex
@@
 
-\title{Compact and widely bandwidth-tunable silicon filter with an unlimited free-spectral range}
+\title{\underline{Compact} and widely bandwidth-tunable silicon filter with an unlimited free-spectral range}
 
@@
 	We measured an out-of-band contrast of up to 55 dB, low in-band ripples of less than 0.3 dB, and in-band group delay variation of less than 8 ps.
-	This result was achieved using cascaded Bragg-grating-assisted contra-directional couplers and micro-heaters on the 220-nm silicon-on-insulator platform with a footprint of less than 7,000~\textmu m$^2$.
-Another design with the bandwidth continuously tunable from 50 GHz to 1 THz is also presented.
+	This result was achieved using cascaded Bragg-grating-assisted contra-directional couplers and micro-heaters on the 220-nm silicon-on-insulator platform with a footprint of less than \underline{7,000~\textmu m$^2$.} Another design with the bandwidth continuously tunable from 50 GHz to 1 THz is also presented.
 \end{abstract}
@@
 	The drop port of the first contra-DC is connected to the input port of the second contra-DC. 
-	Therefore, the finally dropped signal("Drop port of the system"), is determined by the product of the  drop-port transfer functions of the two contra-DCs.
+	Therefore, the finally dropped signal ("Drop port of the system"), is determined by the product of the  drop-port transfer functions of the two contra-DCs.
 
-	%The center wavelength of the contra-DC is determined by the phase-match condition: $\lambda_\text{c} = \Lambda (n_\text{1}+n_\text{2})$, where $\Lambda$ is the grating pitch, and $n_\text{1}$ and $n_\text{2}$ are the effective indices of the first-order and second-order eigenmodes in the coupler.
+	\sout{The center wavelength of the contra-DC is determined by the phase-match condition: $\lambda_\text{c} = \Lambda (n_\text{1}+n_\text{2})$, where $\Lambda$ is the grating pitch, and $n_\text{1}$ and $n_\text{2}$ are the effective indices of the first-order and second-order eigenmodes in the coupler.}
 	At first, the two filters are identical and drop a large, well-defined window.
@@
 	The device was fabricated using a CMOS-compatible technology with electron-beam lithography. 
-	Large coupling coefficients and precise apodization profiles are easier to achieve with this process, although optical lithography able to resolve the required periodicity and gap between waveguides as seen in \ref{fig:SEM} a) could be used.
-The corrugations do not need to be square shaped, but must have a large enough amplitude
-	.
+	\uline{Large coupling coefficients and precise apodization profiles are easier to achieve with this process, although optical lithography able to create the required periodicity and gap between waveguides as seen in \ref{fig:SEM} a) could be used.
+The corrugations do not need to be square shaped, but must have a large enough amplitude.}
+
 	Fiber grating couplers \cite{zhong2014focusingFGC} are used as optical inputs and outputs in the measurement. 
@@
 	The insertion loss is very low, less than 0.5 dB (i.e., 0.25 dB per contra-DC), with small ripples of less than 0.3 dB within the 1-dB passband over 5.8 nm (733~GHz).
+\uline{This agrees with the measurements in the literature \cite{caverley2015measurement}.}
 	The edge roll-off rate is 19 dB/nm on the left side and 24 dB/nm on the right side.
@@
 	Due to the wavelength detuning,  the stop-band edges are now determined by the single filters. 
-	As a result, the side-lobes suppression for small bandwidths degrades to -15 dB.
+	\uline{As a result, the side-lobes suppression for small bandwidths degrades to -15 dB.}
 	A continuous tuning of the 3-dB bandwidth from 788 GHz down to 117 GHz (i.e., over 670 GHz or 5.4 nm) is experimentally observed as the on-chip temperature increases by 70 degrees.
@@
 	The microheaters are made of 300-nm-thick, 2-\textmu m-wide Al strips.
-	The power efficiency of the bandwidth tuning is about 24~mW/nm, which dissipates a lot of heat and would be impractical for integration with electronics.
+	\uline{The power efficiency of the bandwidth tuning is about 24~mW/nm, which dissipates a lot of heat and would be impractical for integration with electronics.}
 	We also observe a slight red-shift of the center wavelength at higher temperature, indicating thermal coupling between the two contra-DCs that are about 10 \textmu m away from each other.
-	These issues can be resolved by optimizing the heater design, e.g., using smaller heater features and thermal isolation \cite{dong2010thermally}.
+	\uline{These issues can be resolved by optimizing the heater design, e.g., using smaller heater features and thermal isolation \cite{dong2010thermally}.}
 
@@
 			\\
-			\textbf{This experiment }& Cascaded contra-DC &	778 GHz / Unlimited  &	67-778 GHz &	0.5 dB / 0.3 dB &	15-55 dB 
+			\textbf{This experiment }& Cascaded contra-DC &	778 GHz / Unlimited  &	67-778 GHz &	0.5 dB / 0.3 dB &	\underline{15-55 dB }
 			\\
